---
title: 'EDA HW1: Serie A League Analysis for AS Roma'
author: 'Group 6: Kexin Liang, Nitin Wahie, Chia-Hsuan Chou, Patrick Hoban, Rekha
  Mohandass, Aadarsh Gupta'
date: "9/28/2019"
output:
  pdf_document: 
    df_print: paged
    latex_engine: xelatex
toc: true
---


### Introduction  
We have been tasked by the coach of the futbol team AS Roma to find non-obvious patterns that he can exploit to increase success for his team on the field. 

Serie A is the professional Italian futbol league in which AS Roma competes. The league is comprised of 20 teams in the first division. Each team is awarded 3 points for a win, 1 point for a draw and 0 points for a loss for every game during the regular season. 

Dataset is pulled from EA Sports.  EA Sports FIFA is annually one of the best selling games in the world.  In 2019 EA sold 20 million units ($1,200,000,000 in estimated sales) of their popular FIFA '19 video game and another 3 million units ($120,000,000 US dollars) of the 2018 version FIFA '18.  The broad appeal of the game is due in large part to Electronic Arts ability to mimic the real world playing styles, abilities, and visuals of teams around the world.

https://gadgets.ndtv.com/games/news/fifa-19-sales-flat-thanks-to-fifa-18-says-ea-1989300

### Complication
Wins are necessary for AS Roma, not only to remain in the Serie A league, but also to improve club profitability. Beyond the obvious merchandising and television broadcast benefits that come with a winning record, Serie A also boasts total prize money of nearly 1 billion euros each year. The top 4 teams in the Serie A each year advance to the UEFA Champions League where an additional 1.3 billion euros is dispersed among the competing teams. 12.7 million euros of which is provided to each team upon qualifying. 5th and 6th place teams in Serie A each year qualify for the UEFA Europa Cup where teams earn 2.6 million euros with bonuses of 360k euros per win.

https://en.wikipedia.org/wiki/Serie_A
https://en.wikipedia.org/wiki/UEFA_Europa_League
https://en.wikipedia.org/wiki/UEFA_Champions_League
https://www.goal.com/en-us/news/premier-league-tv-prize-money-vs-champions-league-la-liga/2rkcwfj4whaz15b0bhf378l3t


## Question & Approach
### Key Question
Which combination of AS Roma players based on player attributes should we field for each game in order to maximize the number of wins and or points earned during the regular season?

### Approach Outline

* Exploratory analysis to visualize the performance of AS Roma in the Serie A for last 8 seasons as well as key opponents
* Using Team attributes to find patterns associated to AS Roma's performance
* Using Player attributes to find patters associated with Key Oppenent's 
* Recommendations based on the above analyses and observations

## Analysis

#### Data Overview
For this analysis, we look into data present as the following data tables:
** match : Contains each match played in the last 8 seasons
** player_atts attributes : Attributes of all the players 
** team_atts : Attributes for all the teams
** teams : Team IDs for all teams in Europe

```{r, include = 'FALSE'}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(magrittr)
library(ggplot2)
library(tidyr)
library(lubridate)
library(reshape2)
library(arules)
library(arulesViz)
library(RColorBrewer)
```


```{r, include = 'FALSE'}
#setwd('C://Users//nitin//Documents//EDA//HW1//HW 1')
con <- src_sqlite("euro_soccer.sqlite")
country_tbl <- tbl(con, "country")
league_tbl <- tbl(con, "league")
match_tbl <- tbl(con, "match")
player_tbl <- tbl(con, "player")
player_atts_tbl <- tbl(con, "player_attributes")
team_tbl <- tbl(con, "team")
team_atts_tbl <- tbl(con, "team_attributes")

country = country_tbl %>%
  collect()
league = league_tbl %>%
  collect()
match = match_tbl %>%
  collect()
player = player_tbl %>%
  collect()
player_atts = player_atts_tbl %>% 
  collect()
teams = team_tbl %>%
  collect()
team_atts = team_atts_tbl %>%
  collect()

roma <- 'Roma'
roma_record <- team_tbl %>% 
                collect() %>%
                filter(grepl(roma, team_long_name))
roma_home_matches <- match %>%
  filter(home_team_api_id == roma_record$team_api_id) %>%
  mutate(goal_diff = home_team_goal - away_team_goal) %>%
  mutate(type = 'home', opponent = away_team_api_id)
roma_away_matches <- match %>%
  filter(away_team_api_id == roma_record$team_api_id) %>%
  mutate(goal_diff =away_team_goal - home_team_goal) %>%
  mutate(type = 'away', opponent = home_team_api_id)

roma_all_match = rbind(roma_home_matches, roma_away_matches)
roma_all_match$result = as.numeric(roma_all_match$goal_diff)
roma_all_match[roma_all_match$goal_diff > 0, ]$result = 'win'
roma_all_match[roma_all_match$goal_diff < 0, ]$result = 'loss'
roma_all_match[roma_all_match$goal_diff == 0, ]$result = 'draw'
```

### Assumptions / Scope
Pursuing new players and player trades can be an expensive and time consuming with no guarantee that other teams will be willing to accept the terms or for which players they would be willing to trade. As such, initially we scope our analysis down to working only with existing players already on our AS Roma team roster.

In terms of teams and opponents, we will work first to identify opportunities within the existing Serie A league of 20 teams.  Where each season AS Roma will encounter each of the other 19 teams twice, playing once at home and once away for a total of 38 games.

### Exploratory Analysis 
#### How have we been doing previously?  How are we doing currently?  

```{r, include=FALSE}
#### Data Preparation
# Mapping team_api_id to team names
teams_serieA <- data.frame(unique(roma_all_match$away_team_api_id))
team_names_serieA <- merge(teams_serieA, teams, by.x = 'unique.roma_all_match.away_team_api_id.', by.y = 'team_api_id')
team_names_serieA <- team_names_serieA %>% 
  rename(team_api_id = unique.roma_all_match.away_team_api_id.) 

team_names_serieA <- team_names_serieA %>%
  select (team_api_id, team_long_name)


### Using attributes
roma_home_matches_ext <- match %>% 
  filter(home_team_api_id == 8686) %>%
  mutate(game_type = 'Home') %>%
  mutate(goal_difference = abs(home_team_goal - away_team_goal)) %>%
  mutate(match_result = ifelse(home_team_goal - away_team_goal > 0, 'Win', 
                               ifelse(home_team_goal - away_team_goal <0 , 'Loss','Draw'))) %>%
  rename(team_api_id = home_team_api_id) %>%
  rename(team_against_api_id = away_team_api_id)

roma_home_matches_ext <-  roma_home_matches_ext %>% 
  inner_join(team_atts, by = ('team_api_id')) %>%
  select(-team_api_id, -id.y) %>%
  rename(team_api_id = team_against_api_id)

roma_home_matches_with_attr <- roma_home_matches_ext %>%
  left_join(team_names_serieA, by = ('team_api_id')) %>%
  rename(team_against = team_long_name)

## --- ##

roma_away_matches_with_attr <- match %>% 
  filter(away_team_api_id == 8686) %>%
  mutate(game_type = 'Away') %>%
  mutate(goal_difference = abs(home_team_goal - away_team_goal)) %>%
  mutate(match_result = ifelse(home_team_goal - away_team_goal < 0, 'Win', 
                               ifelse(home_team_goal - away_team_goal > 0 , 'Loss','Draw'))) %>%
  rename(team_api_id = away_team_api_id)

roma_away_matches_with_attr <- roma_away_matches_with_attr %>% 
  inner_join(team_atts, by = 'team_api_id') %>%
  select(-team_api_id, -id.y) %>%
  rename(team_api_id = home_team_api_id)

roma_away_matches_with_attr <- roma_away_matches_with_attr %>%
  left_join(team_names_serieA, by = ('team_api_id')) %>%
  rename(team_against = team_long_name)

roma_all_matches_with_attr <- rbind(roma_home_matches_with_attr, roma_away_matches_with_attr)

colnames(roma_all_matches_with_attr)
roma_all_matches_attr <- roma_all_matches_with_attr %>%
  select(season, stage, match_date = date.x,team_against, home_team_goal, away_team_goal, game_type,
         goal_difference,match_result, attribute_date = date.y, buildUpPlaySpeedClass, buildUpPlayDribblingClass, 
         buildUpPlayPassingClass,buildUpPlayPositioningClass, chanceCreationPassingClass,
         chanceCreationCrossingClass, chanceCreationShootingClass, chanceCreationPositioningClass,
         defencePressureClass,defenceAggressionClass,defenceTeamWidthClass,defenceDefenderLineClass) %>%
  mutate(date_diff = abs(as.Date(attribute_date) - as.Date(match_date)))

roma_all_matches_attr_match <- roma_all_matches_attr %>%
  group_by(match_date) %>%
  top_n(-1,wt=date_diff)

roma_all_matches_attr_match_clean <- roma_all_matches_attr_match %>%
  select(-date_diff, -attribute_date,) %>%
  mutate(  buildUpPlaySpeedClass = paste(buildUpPlaySpeedClass, "buildUpPlaySpeedClass", sep = "."), 
           buildUpPlayDribblingClass = paste(buildUpPlayDribblingClass, "buildUpPlayDribblingClass", sep = "."), 
           buildUpPlayPassingClass = paste(buildUpPlayPassingClass, "buildUpPlayPassingClass", sep = "."),
           buildUpPlayPositioningClass = paste(buildUpPlayPositioningClass, "buildUpPlayPositioningClass", sep = "."), 
           chanceCreationPassingClass = paste(chanceCreationPassingClass, "chanceCreationPassingClass", sep = "."),
           chanceCreationCrossingClass = paste(chanceCreationCrossingClass, "chanceCreationCrossingClass", sep = "."), 
           chanceCreationShootingClass = paste(chanceCreationShootingClass, "chanceCreationShootingClass", sep = "."), 
           chanceCreationPositioningClass = paste(chanceCreationPositioningClass, "chanceCreationPositioningClass", sep = "."),
           defencePressureClass = paste(defencePressureClass, "defencePressureClass", sep = "."),
           defenceAggressionClass = paste(defenceAggressionClass, "defenceAggressionClass", sep = "."),
           defenceTeamWidthClass = paste(defenceTeamWidthClass, "defenceTeamWidthClass", sep = "."),
           defenceDefenderLineClass = paste(defenceDefenderLineClass, "defenceDefenderLineClass", sep = "."))


roma_all_matches_clean <- roma_all_matches_attr_match %>%
  select(-date_diff, -attribute_date, -team_against, -stage, -season) 


```
    
##### Roma League Performance from 2008/09 - 2015/16  

```{r, echo = FALSE}
 # Roma wins and losses over the seasons
  # ggplot(roma_matches_lost_by_seasons, aes(x = season, y = losses)) + 
  #   geom_bar(stat = 'identity', position = 'dodge')
  
  library(scales)


#Roma performance every season
ggplot(roma_all_matches_attr_match, aes(x = season, fill = match_result)) + 
  geom_bar( position = 'fill') + 
  scale_y_continuous(labels = percent_format(), limits=c(0,1))+
  ylab('% of games')+ xlab('League season')+ theme_classic()+
  scale_fill_manual("legend", values = c('Win' = 'Beige', 'Draw' = 'gold', 'Loss' ='dark red'))+
  labs(title = "AS Roma League Performance ")

```
  
  
We first look at AS Roma's performance in Serie A over the last 8 league seasons and find out that we win close to 50% of games every season. We also see that our win percentage has gone up in the last three seasons on an average, with fewer losses. 
Moreover, the number of drawn games has increased in the last two seasons, with more than 10 games drawn in these seasons.


##### Roma League performance by Stages in a season  

```{r}
# Matches played before May 2012
ggplot(roma_all_matches_attr_match %>% 
         filter(match_date < '2012-05-30'), aes(x = stage, fill = match_result)) +
  geom_bar( position = 'fill')+ theme_classic() +
  ylab('% Games') + 
  scale_y_continuous(labels = percent_format(), limits=c(0,1)) + 
  labs(title = "Roma performance across stages in a season (2008 - 2012)") +
  scale_fill_manual("legend", values = c('Win' = 'beige', 'Draw' = 'gold', 
                                         'Loss' ='dark red'))

```

  Looking across the length of the season gives us interesting readings. In the season from 2008 to 2012, Roma used to have a slow start to the campaign but a strong performance during the middle stages.

```{r}

# Matches played after May 2012
ggplot(roma_all_matches_attr_match %>% 
         filter(match_date > '2012-05-30'), aes(x = stage, fill = match_result)) +
  geom_bar( position = 'fill')+ theme_classic() +
  ylab('% Games') + 
  scale_y_continuous(labels = percent_format(), limits=c(0,1)) +
  labs(title = "Roma performance across stages in a season (2012-2016)") +
  scale_fill_manual("legend", values = c('Win' = 'beige', 'Draw' = 'gold', 
                                         'Loss' ='dark red'))
```
  

However, looking at the last 4 years, we see an almost opposite trend in our performances in the league. In the last 4 seasons, we have started strong, but tend to slow down towards the middle of the season. 
Finally we again pick up some pace towards the end of the season.  


```{r}
#All matches played
ggplot(roma_all_matches_attr_match, aes(x = stage, fill = match_result)) +
  geom_bar( position = 'fill')+ theme_classic() +
  ylab('% Games') + 
  scale_y_continuous(labels = percent_format(), limits=c(0,1)) +
  labs(title = "Roma performance across stages in a season (All Seasons") +
  scale_fill_manual("legend", values = c('Win' = 'beige', 'Draw' = 'gold', 
                                         'Loss' ='dark red'))

```
  
  A key observation when looking at all the games over the last 8 seasons is the number of losses or draws for stage 18. This stage is often around the winter break in the league and may correspond to the fatigue of players.  
    
    

#### What are our biggest challenges?  Who are our key competitors? 

```{r, echo = FALSE}
#  Matches lost and drawn against opponents 
melt_in <- table(roma_all_matches_attr_match$team_against, roma_all_matches_attr_match$match_result)
melted_in <- melt_in %>% melt(id.vars = 'team_against', values = 'match_result')
par(mfrow = c(1,1))
#sorted 
ggplot(melted_in %>% filter(value >2 & Var2 == 'Loss'), aes(reorder(Var1,-value),y = value, fill = Var2))+
  geom_bar(stat = 'identity', alpha = 0.95)+ theme_classic() + 
  xlab('Teams against') +
  ylab('No. of matches')  + 
  scale_fill_manual("legend", values = c( "Loss" = "Dark Red")) +
  labs(title = "Roma Losses against the Serie A teams ") + theme(legend.position = "none")+
  theme(text = element_text(size=10))
```
  
  From the above plot, we see that in the last 8 seasons, we have had the hardest time while facing Juventus, losing 10 of the 16 times we faced them. Other difficult rivals for us have been Sampdoria, Genoa, Napoli and Palermo.  
  

#### Is there a way to adjust Home vs Away Game Performance?

Another idea was to pursue strategy differences between home and away game performance. Looking at wins at home vs wins away there is a distinct difference. We are consistently losing more games away and winning far lesser. 

```{r}
roma_win_match = roma_all_match[roma_all_match$result == 'win',]
roma_win_match = roma_win_match %>%
  select(season, type, result) %>%
  group_by(season, type) %>%
  count(result)

ggplot(roma_win_match, aes(season, n, col = type, group = type)) +
  geom_line() +
  geom_point(size = 1) +
  theme_classic() +
  scale_y_continuous(breaks=seq(0, 15, 1)) +
  scale_color_discrete(name = 'Match Type', breaks = c('home','away'), 
                       labels = c('Home Match', 'Away Match')) +
  labs(x = 'Match Season', y = 'Number of Wins', 
       title = 'Number of Wins per Season for AS ROMA: Home VS Away') +
  theme(plot.title = element_text(size = 12))
```


While this seems like a large gap initially, industry and domain knowledge led us away from pursuing this strategy. While it is widely known that teams will naturally perform better playing at home, as opposed to playing away. And there are many factors that are suspected as contributing to this phenomenon.  
Unfortunately, there are few we would be able to identify and fewer of these environmental factors that we could directly impact or change. The league allows fields to be wider or longer to a certain degree and training and playing on these varying field sizes may prove effective for different strategies, but cost in millions and time of implementation is prohibitive at best for any kind of stadium and practice facility remodeling. Another example for this correlation between home field advantage could be weather and while we pray constantly for AS Roma championships, unfortunately for good reason, we don't foresee God granting us the ability to control weather as a factor.


### Can we identify patterns in team attributes leading to win/loss of AS Roma?
    
Our next thought was to utilize team attributes to identify and set up playing style for the team so that the coach can fit players into the general style. Potentially you could fit many different players into any one playing style leaving more flexibility in approach. For instance, if we could utilize our best players and train them to play a specific style for each game, this would be far less limiting than a strategy that expanded to potentially require player trades.

However, as we began to explore the data, we quickly found that team attributes data start only in 2010 and change out only once per year. As such, predicting a season with the same set of players, would not allow you to see any changes. Predicting team attributes across multiple seasons with a low threshold and support, you start to see some variables appear more consistently.
    
We still tried to run the association rules on these team attributes, and the results are shown below.
  
  
#### Finding associations from the Team attributes that lead to Roma Win
```{r, include=FALSE}
options(warn=-1)

roma_all_matches_clean_rules <- roma_all_matches_clean %>%
  select(-match_date, -home_team_goal,-away_team_goal, -goal_difference)

roma_all_matches_trans <- as(roma_all_matches_clean_rules,'transactions')

# summary(roma_all_matches_trans)

# Get the frequency of most used item
#itemFrequency(roma_all_matches_trans)


# Creating and running apriori rules on undefined LHS, RHS
association.rules <- apriori(roma_all_matches_trans, parameter = list(supp = 0.01, conf = 0.8 ))
# summary(association.rules)

#Printing the top rules
# inspect(association.rules[1:10])

# Creating and running apriori rules on RHS = Win
association.rules.2 <- apriori(roma_all_matches_trans,parameter = list(supp = 0.09, conf = 0.7,maxlen = 5 ), appearance = list(rhs = 'match_result=Win'))
# inspect(association.rules.2[1:40])
```

```{r}
# Plotting parallel coords fro apriori rules to visualize
plot(association.rules.2, method = 'paracoord')
```
  
  Running the rules based on Roma's wins resulted in too many rules all mixed together (even with a low threshold), indicating that there may be absence of any pattern in our wins, or to put it plainly, any of the above combinations (as specified by the y-axis in the plot above) could result in a win for us if we play at home. 
  
  
#### Finding associations from the Team attributes that lead to Roma Loss
```{r, include=FALSE}

#Apriori rules on RHS = Loss
association.rules.3 <- apriori(roma_all_matches_trans,
                       parameter = list(supp = 0.15,
                       conf = 0.25,maxlen = 5 ), 
                       appearance = list(rhs = 'match_result=Loss'))
                       
# inspect(association.rules.3[1:3])
```

```{r}
#Plotting parallel coords for apriori rules to visualize 
plot(association.rules.3, method = 'paracoord') 
 
```
  
  We then tested on the the matches AS Roma loses. As the graph suggests, the medium defence pressure, shooting chance creation and playing as away team lead to loss. However, it's difficult to plan strategy based on the medium metrics. Also, we already know that playing as away team naturally create weakness to the team.
  
  

### Can we identify patterns in player attributes leading to win/loss of any team?  

We then moved to identify attributes of the players that serve as ingredients in deciding at match's result. In this case, wanted to find the weaknesses of our top opponents that could help us set up team to get a positive result next time when we face them. 

#### Is there a specific set of player attributes that appear more frequently and correlate with one of our opponents losing a match?

Since the team attributes cannot provide sufficient information for strategic plan, we decided to dive deeper to see if for a certain opposing team, there were specific combinations of player attributes by position the coach could mimic to in order to defeat the opponent.

We found out AS Roma loses most often to Juventus in previous exploratory analysis, so we ran association rule against it first. Below we perform data transformation to arrive at the format of transactions we need to perform association nanalysis.
    
#### Data Transformation

We will evaluate a transaction as each match in our data set that resulted in an opponent losing that match.
For example, as Juventus is the team we lose most matches to, we look into what combination of player attributes leads to Juventus loss.

  LHS: 38 Player Attributes of Opposing Team
  RHS: Juventus Loss

In order to achieve the association rules above, we need to transform the original data into transaction data format first.


##### Filtering out all the matches that Juventus participates

We filter all the matches Juventus participates throughout the years, and add the result label based on the goal difference in the data.

```{r}
juventus = 'Juventus'
juventus_record <- team_tbl %>% 
                    collect() %>%
                    filter(grepl(juventus, team_long_name))

juventus_home_matches <- match %>%
  filter(home_team_api_id == juventus_record$team_api_id) %>%
  mutate(goal_diff = home_team_goal - away_team_goal) %>%
  mutate(type = 'home', opponent = away_team_api_id)

juventus_away_matches <- match %>%
  filter(away_team_api_id == juventus_record$team_api_id) %>%
  mutate(goal_diff =away_team_goal - home_team_goal) %>%
  mutate(type = 'away', opponent = home_team_api_id)

all_match = rbind(juventus_home_matches, juventus_away_matches)
all_match$result = as.numeric(all_match$goal_diff)
all_match[all_match$goal_diff > 0, ]$result = 'win'
all_match[all_match$goal_diff < 0, ]$result = 'loss'
all_match[all_match$goal_diff == 0, ]$result = 'draw'

```
  
##### Map the position of player based on his X, Y coordinates on the field
Then, we use the X, Y coordinate provided to categorize the player's position. If (x, y) = (1, 1), the player is a goal keeper; if 2 ≤ y ≤ 5, the player is a defender; if 6 ≤ y ≤ 8, he is a mid fielder, and if 9 ≤ y ≤ 11, he is a forwarder(striker).
```{r}
for (i in 1:11){
  x = paste("home_player_X",i,sep='')
  y = paste("home_player_Y",i,sep='')
  inp = paste("hm_ply_pos",i,sep="_")
  all_match[inp] = ifelse(all_match[x]==1 & all_match[y]==1,"Goaly",
                      ifelse(all_match[y]>=2 & all_match[y]<=5,"Defender",
                             ifelse(all_match[y]>=6 & all_match[y]<=8,"Mid Fielders",
                                    ifelse(all_match[y]>=9 & all_match[y]<=11,
                                           "Forwards","NA"))))
}

for (i in 1:11){
  x = paste("away_player_X",i,sep='')
  y = paste("away_player_Y",i,sep='')
  inp = paste("away_ply_pos",i,sep="_")
  all_match[inp] = ifelse(all_match[x]==1 & all_match[y]==1,"Goaly",
                      ifelse(all_match[y]>=2 & all_match[y]<=5,"Defender",
                             ifelse(all_match[y]>=6 & all_match[y]<=8,"Mid Fielders",
                                    ifelse(all_match[y]>=9 & all_match[y]<=11,
                                    "Forwards","NA"))))
}

```

##### Categorizing Player attributes:
Attributes are currently ranked on a 0 to 100 scale.  We will take min / max for each attribute, then divide the range into 5 categories. This will create a low, low-med, med, med-high, high value for each attribute.

```{r}
column_names = c("overall_rating","potential","crossing", "finishing","heading_accuracy",    
                 "short_passing", "volleys","dribbling",    
                 "curve", "free_kick_accuracy" ,"long_passing",    
                 "ball_control","acceleration","sprint_speed",    
                 "agility","reactions","balance",    
                 "shot_power","jumping","stamina",    
                 "strength","long_shots","aggression",    
                 "interceptions","positioning","vision",    
                 "penalties", "marking","standing_tackle",
                 "sliding_tackle","gk_diving","gk_handling",    
                 "gk_kicking","gk_positioning","gk_reflexes")
for (i in column_names){
  k = paste(i, "Bucket",sep="_")
  player_atts[k] = 
    cut(player_atts[[i]], breaks = 5, labels=c('low','low-med','med','med-high','high'))
}

player_atts <- select(player_atts, c(1:9, overall_rating_Bucket:gk_reflexes_Bucket))
player_atts = player_atts[, -c(5,6)]
all_match <- select(all_match, c(id:away_team_goal, home_player_1:away_player_11, 
                                 opponent:away_ply_pos_11))

```


##### Merge player attributes to matches by taking the player attribute records closest to the particular match time
Since we already have a categorical player attributes table and a Juventus match table, next we merge these two table into the final table where one row represents one match along with attributes of both 11 home players and 11 away players. For each player in each match, we select the record of his attributes closest to that particular match date, and comebine his position and 38 attributes together into one cell. We show the data manipulation for home player 1, and repeat the similar process to other 21 players (which we hide the repeated codes).

```{r}
#HP1
match_player <- merge(x = all_match, y=player_atts,by.x='home_player_1',
                      by.y='player_api_id',all.x=TRUE)
match_player$date.x<-ymd_hms(match_player$date.x)
match_player$date.y<-ymd_hms(match_player$date.y)
match_player$time_diff <- difftime(match_player$date.x, match_player$date.y,units='days')
match_player = match_player[match_player$time_diff >= 0,]
match_player_1 = match_player %>%
  group_by(match_api_id, home_player_1) %>%
  filter(time_diff == min(time_diff))
for (i in 61:98){
  colnames(match_player_1)[i] = paste(colnames(match_player_1)[i], "hp_1", sep = "_")
}
for (i in 61:98){
  match_player_1[[i]] = paste(match_player_1[[i]],match_player_1[[36]],sep="_")
}
match_player_1$time_diff=NULL

```

```{r, include= FALSE}
# HP2

match_player2 <- merge(x = match_player_1, y=player_atts,by.x='home_player_2',by.y='player_api_id',all.x=TRUE)
match_player2$date.x<-ymd(match_player2$date.x)
match_player2$date<-ymd_hms(match_player2$date)
match_player2$time_diff <- difftime(match_player2$date.x, match_player2$date,units='days')
match_player2 = match_player2[match_player2$time_diff >= 0,]
match_player2 = match_player2 %>%
  group_by(match_api_id, home_player_2) %>%
  filter(time_diff == min(time_diff))
for (i in 102:139){
  colnames(match_player2)[i] = paste(colnames(match_player2)[i], "hp_2", sep = "_")
}
for (i in 102:139){
  match_player2[[i]] = paste(match_player2[[i]],match_player2[[37]],sep="_")
}
match_player2$time_diff=NULL
match_player2$id.y = NULL
match_player2$date.y=NULL
match_player2$date=NULL
match_player2$id.x=NULL
##
#HP3

match_player3 <- merge(x = match_player2, y=player_atts,by.x='home_player_3',by.y='player_api_id',all.x=TRUE)
match_player3$date.x<-ymd(match_player3$date.x)
match_player3$date<-ymd_hms(match_player3$date)
match_player3$time_diff <- difftime(match_player3$date.x, match_player3$date,units='days')
match_player3 = match_player3[match_player3$time_diff >= 0,]
match_player3 = match_player3 %>%
  group_by(match_api_id, home_player_3) %>%
  filter(time_diff == min(time_diff))
for (i in 139:176){
  colnames(match_player3)[i] = paste(colnames(match_player3)[i], "hp_3", sep = "_")
}
for (i in 139:176){
  match_player3[[i]] = paste(match_player3[[i]],match_player3[[37]],sep="_")
}
match_player3$time_diff=NULL
match_player3$id.y = NULL
match_player3$date.y=NULL
match_player3$date=NULL
match_player3$id.x=NULL
match_player3$player_fifa_api_id=NULL

#HP4

match_player4 <- merge(x = match_player3, y=player_atts,by.x='home_player_4',by.y='player_api_id',all.x=TRUE)
match_player4$date.x<-ymd(match_player4$date.x)
match_player4$date<-ymd_hms(match_player4$date)
match_player4$time_diff <- difftime(match_player4$date.x, match_player4$date,units='days')
match_player4 = match_player4[match_player4$time_diff >= 0,]
match_player4 = match_player4 %>%
  group_by(match_api_id, home_player_4) %>%
  filter(time_diff == min(time_diff))
for (i in 176:213){
  colnames(match_player4)[i] = paste(colnames(match_player4)[i], "hp_4", sep = "_")
}
for (i in 176:213){
  match_player4[[i]] = paste(match_player4[[i]],match_player4[[38]],sep="_")
}
match_player4$time_diff=NULL
match_player4$id.y = NULL
match_player4$date.y=NULL
match_player4$date=NULL
match_player4$id.x=NULL
match_player4$id=NULL
match_player4$player_fifa_api_id.x=NULL
match_player4$player_fifa_api_id.y=NULL
#HP5

match_player5 <- merge(x = match_player4, y=player_atts,by.x='home_player_5',by.y='player_api_id',all.x=TRUE)
match_player5$date.x<-ymd(match_player5$date.x)
match_player5$date<-ymd_hms(match_player5$date)
match_player5$time_diff <- difftime(match_player5$date.x, match_player5$date,units='days')
match_player5 = match_player5[match_player5$time_diff >= 0,]
match_player5 = match_player5 %>%
  group_by(match_api_id, home_player_5) %>%
  filter(time_diff == min(time_diff))
for (i in 213:250){
  colnames(match_player5)[i] = paste(colnames(match_player5)[i], "hp_5", sep = "_")
}
for (i in 213:250){
  match_player5[[i]] = paste(match_player5[[i]],match_player5[[39]],sep="_")
}
match_player5$time_diff=NULL
match_player5$id.y = NULL
match_player5$date.y=NULL
match_player5$date=NULL
match_player5$id.x=NULL
match_player5$id=NULL
###
#HP6
match_player6 <- merge(x = match_player5, y=player_atts,by.x='home_player_6',by.y='player_api_id',all.x=TRUE)
match_player6$date.x<-ymd(match_player6$date.x)
match_player6$date<-ymd_hms(match_player6$date)
match_player6$time_diff <- difftime(match_player6$date.x, match_player6$date,units='days')
match_player6 = match_player6[match_player6$time_diff >= 0,]
match_player6 = match_player6 %>%
  group_by(match_api_id, home_player_6) %>%
  filter(time_diff == min(time_diff))
for (i in 252:289){
  colnames(match_player6)[i] = paste(colnames(match_player6)[i], "hp_6", sep = "_")
}
for (i in 252:289){
  match_player6[[i]] = paste(match_player6[[i]],match_player6[[40]],sep="_")
}
match_player6$time_diff=NULL
match_player6$id.y = NULL
match_player6$date.y=NULL
match_player6$date=NULL
match_player6$id.x=NULL
match_player6$id=NULL
match_player6$player_fifa_api_id.x=NULL
match_player6$player_fifa_api_id.y=NULL

#HP7
match_player7 <- merge(x = match_player6, y=player_atts,by.x='home_player_7',by.y='player_api_id',all.x=TRUE)
match_player7$date.x<-ymd(match_player7$date.x)
match_player7$date<-ymd_hms(match_player7$date)
match_player7$time_diff <- difftime(match_player7$date.x, match_player7$date,units='days')
match_player7 = match_player7[match_player7$time_diff >= 0,]
match_player7 = match_player7 %>%
  group_by(match_api_id, home_player_7) %>%
  filter(time_diff == min(time_diff))
for (i in 289:326){
  colnames(match_player7)[i] = paste(colnames(match_player7)[i], "hp_7", sep = "_")
}
for (i in 289:326){
  match_player7[[i]] = paste(match_player7[[i]],match_player7[[41]],sep="_")
}
match_player7$time_diff=NULL
match_player7$id.y = NULL
match_player7$date.y=NULL
match_player7$date=NULL
match_player7$id.x=NULL
match_player7$id=NULL
match_player7$player_fifa_api_id.x=NULL
match_player7$player_fifa_api_id.y=NULL

#HP8
match_player8 <- merge(x = match_player7, y=player_atts,by.x='home_player_8',by.y='player_api_id',all.x=TRUE)
match_player8$date.x<-ymd(match_player8$date.x)
match_player8$date<-ymd_hms(match_player8$date)
match_player8$time_diff <- difftime(match_player8$date.x, match_player8$date,units='days')
match_player8 = match_player8[match_player8$time_diff >= 0,]
match_player8 = match_player8 %>%
  group_by(match_api_id, home_player_8) %>%
  filter(time_diff == min(time_diff))
for (i in 326:363){
  colnames(match_player8)[i] = paste(colnames(match_player8)[i], "hp_8", sep = "_")
}
for (i in 326:363){
  match_player8[[i]] = paste(match_player8[[i]],match_player8[[42]],sep="_")
}
match_player8$time_diff=NULL
match_player8$id.y = NULL
match_player8$date.y=NULL
match_player8$date=NULL
match_player8$id.x=NULL
match_player8$id=NULL
match_player8$player_fifa_api_id.x=NULL
match_player8$player_fifa_api_id.y=NULL

#HP9
match_player9 <- merge(x = match_player8, y=player_atts,by.x='home_player_9',by.y='player_api_id',all.x=TRUE)
match_player9$date.x<-ymd(match_player9$date.x)
match_player9$date<-ymd_hms(match_player9$date)
match_player9$time_diff <- difftime(match_player9$date.x, match_player9$date,units='days')
match_player9 = match_player9[match_player9$time_diff >= 0,]
match_player9 = match_player9 %>%
  group_by(match_api_id, home_player_9) %>%
  filter(time_diff == min(time_diff))
for (i in 365:402){
  colnames(match_player9)[i] = paste(colnames(match_player9)[i], "hp_9", sep = "_")
}
for (i in 365:402){
  match_player9[[i]] = paste(match_player9[[i]],match_player9[[43]],sep="_")
}
match_player9$time_diff=NULL
match_player9$id.y = NULL
match_player9$date.y=NULL
match_player9$date=NULL
match_player9$id.x=NULL
match_player9$id=NULL
match_player9$player_fifa_api_id.x=NULL
match_player9$player_fifa_api_id.y=NULL

#HP10
match_player10 <- merge(x = match_player9, y=player_atts,by.x='home_player_10',by.y='player_api_id',all.x=TRUE)
match_player10$date.x<-ymd(match_player10$date.x)
match_player10$date<-ymd_hms(match_player10$date)
match_player10$time_diff <- difftime(match_player10$date.x, match_player10$date,units='days')
match_player10 = match_player10[match_player10$time_diff >= 0,]
match_player10 = match_player10 %>%
  group_by(match_api_id, home_player_10) %>%
  filter(time_diff == min(time_diff))
for (i in 402:439){
  colnames(match_player10)[i] = paste(colnames(match_player10)[i], "hp_10", sep = "_")
}
for (i in 402:439){
  match_player10[[i]] = paste(match_player10[[i]],match_player10[[44]],sep="_")
}
match_player10$time_diff=NULL
match_player10$id.y = NULL
match_player10$date.y=NULL
match_player10$date=NULL
match_player10$id.x=NULL
match_player10$id=NULL
match_player10$player_fifa_api_id.x=NULL
match_player10$player_fifa_api_id.y=NULL

#HP11
match_player11 <- merge(x = match_player10, y=player_atts,by.x='home_player_11',by.y='player_api_id',all.x=TRUE)
match_player11$date.x<-ymd(match_player11$date.x)
match_player11$date<-ymd_hms(match_player11$date)
match_player11$time_diff <- difftime(match_player11$date.x, match_player11$date,units='days')
match_player11 = match_player11[match_player11$time_diff >= 0,]
match_player11 = match_player11 %>%
  group_by(match_api_id, home_player_11) %>%
  filter(time_diff == min(time_diff))
for (i in 441:478){
  colnames(match_player11)[i] = paste(colnames(match_player11)[i], "hp_11", sep = "_")
}
for (i in 441:478){
  match_player11[[i]] = paste(match_player11[[i]],match_player11[[45]],sep="_")
}
match_player11$time_diff=NULL
match_player11$id.y = NULL
match_player11$date.y=NULL
match_player11$date=NULL
match_player11$id.x=NULL
match_player11$id=NULL
match_player11$player_fifa_api_id.x=NULL
match_player11$player_fifa_api_id.y=NULL

#AP1

match_player12 <- merge(x = match_player11, y=player_atts,by.x='away_player_1',by.y='player_api_id',all.x=TRUE)
match_player12$date.x<-ymd(match_player12$date.x)
match_player12$date<-ymd_hms(match_player12$date)
match_player12$time_diff <- difftime(match_player12$date.x, match_player12$date,units='days')
match_player12 = match_player12[match_player12$time_diff >= 0,]
match_player12 = match_player12 %>%
  group_by(match_api_id, away_player_1) %>%
  filter(time_diff == min(time_diff))
for (i in 478:515){
  colnames(match_player12)[i] = paste(colnames(match_player12)[i], "aw_p_1", sep = "_")
}
for (i in 478:515){
  match_player12[[i]] = paste(match_player12[[i]],match_player12[[46]],sep="_")
}
match_player12$time_diff=NULL
match_player12$id.y = NULL
match_player12$date.y=NULL
match_player12$date=NULL
match_player12$id.x=NULL
match_player12$id=NULL
match_player12$player_fifa_api_id.x=NULL
match_player12$player_fifa_api_id.y=NULL
#AP2
match_player13 <- merge(x = match_player12, y=player_atts,by.x='away_player_2',by.y='player_api_id',all.x=TRUE)
match_player13$date.x<-ymd(match_player13$date.x)
match_player13$date<-ymd_hms(match_player13$date)
match_player13$time_diff <- difftime(match_player13$date.x, match_player13$date,units='days')
match_player13 = match_player13[match_player13$time_diff >= 0,]
match_player13 = match_player13 %>%
  group_by(match_api_id, away_player_2) %>%
  filter(time_diff == min(time_diff))
for (i in 517:554){
  colnames(match_player13)[i] = paste(colnames(match_player13)[i], "aw_p_2", sep = "_")
}
for (i in 517:554){
  match_player13[[i]] = paste(match_player13[[i]],match_player13[[47]],sep="_")
}
match_player13$time_diff=NULL
match_player13$id.y = NULL
match_player13$date.y=NULL
match_player13$date=NULL
match_player13$id.x=NULL
match_player13$id=NULL
match_player13$player_fifa_api_id.x=NULL
match_player13$player_fifa_api_id.y=NULL

#AP3
match_player14 <- merge(x = match_player13, y=player_atts,by.x='away_player_3',by.y='player_api_id',all.x=TRUE)
match_player14$date.x<-ymd(match_player14$date.x)
match_player14$date<-ymd_hms(match_player14$date)
match_player14$time_diff <- difftime(match_player14$date.x, match_player14$date,units='days')
match_player14 = match_player14[match_player14$time_diff >= 0,]
match_player14 = match_player14 %>%
  group_by(match_api_id, away_player_3) %>%
  filter(time_diff == min(time_diff))
for (i in 554:591){
  colnames(match_player14)[i] = paste(colnames(match_player14)[i], "aw_p_3", sep = "_")
}
for (i in 554:591){
  match_player14[[i]] = paste(match_player14[[i]],match_player14[[48]],sep="_")
}
match_player14$time_diff=NULL
match_player14$id.y = NULL
match_player14$date.y=NULL
match_player14$date=NULL
match_player14$id.x=NULL
match_player14$id=NULL
match_player14$player_fifa_api_id.x=NULL
match_player14$player_fifa_api_id.y=NULL

#AP4
match_player15 <- merge(x = match_player14, y=player_atts,by.x='away_player_4',by.y='player_api_id',all.x=TRUE)
match_player15$date.x<-ymd(match_player15$date.x)
match_player15$date<-ymd_hms(match_player15$date)
match_player15$time_diff <- difftime(match_player15$date.x, match_player15$date,units='days')
match_player15 = match_player15[match_player15$time_diff >= 0,]
match_player15 = match_player15 %>%
  group_by(match_api_id, away_player_4) %>%
  filter(time_diff == min(time_diff))
for (i in 593:630){
  colnames(match_player15)[i] = paste(colnames(match_player15)[i], "aw_p_4", sep = "_")
}
for (i in 593:630){
  match_player15[[i]] = paste(match_player15[[i]],match_player15[[49]],sep="_")
}
match_player15$time_diff=NULL
match_player15$id.y = NULL
match_player15$date.y=NULL
match_player15$date=NULL
match_player15$id.x=NULL
match_player15$id=NULL
match_player15$player_fifa_api_id.x=NULL
match_player15$player_fifa_api_id.y=NULL

#AP5
match_player16 <- merge(x = match_player15, y=player_atts,by.x='away_player_5',by.y='player_api_id',all.x=TRUE)
match_player16$date.x<-ymd(match_player16$date.x)
match_player16$date<-ymd_hms(match_player16$date)
match_player16$time_diff <- difftime(match_player16$date.x, match_player16$date,units='days')
match_player16 = match_player16[match_player16$time_diff >= 0,]
match_player16 = match_player16 %>%
  group_by(match_api_id, away_player_5) %>%
  filter(time_diff == min(time_diff))
for (i in 630:667){
  colnames(match_player16)[i] = paste(colnames(match_player16)[i], "aw_p_5", sep = "_")
}
for (i in 630:667){
  match_player16[[i]] = paste(match_player16[[i]],match_player16[[50]],sep="_")
}
match_player16$time_diff=NULL
match_player16$id.y = NULL
match_player16$date.y=NULL
match_player16$date=NULL
match_player16$id.x=NULL
match_player16$id=NULL
match_player16$player_fifa_api_id.x=NULL
match_player16$player_fifa_api_id.y=NULL
#AP6
match_player17 <- merge(x = match_player16, y=player_atts,by.x='away_player_6',by.y='player_api_id',all.x=TRUE)
match_player17$date.x<-ymd(match_player17$date.x)
match_player17$date<-ymd_hms(match_player17$date)
match_player17$time_diff <- difftime(match_player17$date.x, match_player17$date,units='days')
match_player17 = match_player17[match_player17$time_diff >= 0,]
match_player17 = match_player17 %>%
  group_by(match_api_id, away_player_6) %>%
  filter(time_diff == min(time_diff))
for (i in 669:706){
  colnames(match_player17)[i] = paste(colnames(match_player17)[i], "aw_p_6", sep = "_")
}
for (i in 669:706){
  match_player17[[i]] = paste(match_player17[[i]],match_player17[[51]],sep="_")
}
match_player17$time_diff=NULL
match_player17$id.y = NULL
match_player17$date.y=NULL
match_player17$date=NULL
match_player17$id.x=NULL
match_player17$id=NULL
match_player17$player_fifa_api_id.x=NULL
match_player17$player_fifa_api_id.y=NULL
#AP7
match_player18 <- merge(x = match_player17, y=player_atts,by.x='away_player_7',by.y='player_api_id',all.x=TRUE)
match_player18$date.x<-ymd(match_player18$date.x)
match_player18$date<-ymd_hms(match_player18$date)
match_player18$time_diff <- difftime(match_player18$date.x, match_player18$date,units='days')
match_player18 = match_player18[match_player18$time_diff >= 0,]
match_player18 = match_player18 %>%
  group_by(match_api_id, away_player_7) %>%
  filter(time_diff == min(time_diff))
for (i in 706:743){
  colnames(match_player18)[i] = paste(colnames(match_player18)[i], "aw_p_7", sep = "_")
}
for (i in 706:743){
  match_player18[[i]] = paste(match_player18[[i]],match_player18[[52]],sep="_")
}
match_player18$time_diff=NULL
match_player18$id.y = NULL
match_player18$date.y=NULL
match_player18$date=NULL
match_player18$id.x=NULL
match_player18$id=NULL
match_player18$player_fifa_api_id.x=NULL
match_player18$player_fifa_api_id.y=NULL
#AP8
match_player19 <- merge(x = match_player18, y=player_atts,by.x='away_player_8',by.y='player_api_id',all.x=TRUE)
match_player19$date.x<-ymd(match_player19$date.x)
match_player19$date<-ymd_hms(match_player19$date)
match_player19$time_diff <- difftime(match_player19$date.x, match_player19$date,units='days')
match_player19 = match_player19[match_player19$time_diff >= 0,]
match_player19 = match_player19 %>%
  group_by(match_api_id, away_player_8) %>%
  filter(time_diff == min(time_diff))
for (i in 745:782){
  colnames(match_player19)[i] = paste(colnames(match_player19)[i], "aw_p_8", sep = "_")
}
for (i in 745:782){
  match_player19[[i]] = paste(match_player19[[i]],match_player19[[53]],sep="_")
}
match_player19$time_diff=NULL
match_player19$id.y = NULL
match_player19$date.y=NULL
match_player19$date=NULL
match_player19$id.x=NULL
match_player19$id=NULL
match_player19$player_fifa_api_id.x=NULL
match_player19$player_fifa_api_id.y=NULL
#AP9
match_player20 <- merge(x = match_player19, y=player_atts,by.x='away_player_9',by.y='player_api_id',all.x=TRUE)
match_player20$date.x<-ymd(match_player20$date.x)
match_player20$date<-ymd_hms(match_player20$date)
match_player20$time_diff <- difftime(match_player20$date.x, match_player20$date,units='days')
match_player20 = match_player20[match_player20$time_diff >= 0,]
match_player20 = match_player20 %>%
  group_by(match_api_id, away_player_9) %>%
  filter(time_diff == min(time_diff))
for (i in 782:819){
  colnames(match_player20)[i] = paste(colnames(match_player20)[i], "aw_p_9", sep = "_")
}
for (i in 782:819){
  match_player20[[i]] = paste(match_player20[[i]],match_player20[[54]],sep="_")
}
match_player20$time_diff=NULL
match_player20$id.y = NULL
match_player20$date.y=NULL
match_player20$date=NULL
match_player20$id.x=NULL
match_player20$id=NULL
match_player20$player_fifa_api_id.x=NULL
match_player20$player_fifa_api_id.y=NULL
#AP10
match_player21 <- merge(x = match_player20, y=player_atts,by.x='away_player_10',by.y='player_api_id',all.x=TRUE)
match_player21$date.x<-ymd(match_player21$date.x)
match_player21$date<-ymd_hms(match_player21$date)
match_player21$time_diff <- difftime(match_player21$date.x, match_player21$date,units='days')
match_player21 = match_player21[match_player21$time_diff >= 0,]
match_player21 = match_player21 %>%
  group_by(match_api_id, away_player_10) %>%
  filter(time_diff == min(time_diff))
for (i in 821:858){
  colnames(match_player21)[i] = paste(colnames(match_player21)[i], "aw_p_10", sep = "_")
}
for (i in 821:858){
  match_player21[[i]] = paste(match_player21[[i]],match_player21[[55]],sep="_")
}
match_player21$time_diff=NULL
match_player21$id.y = NULL
match_player21$date.y=NULL
match_player21$date=NULL
match_player21$id.x=NULL
match_player21$id=NULL
match_player21$player_fifa_api_id.x=NULL
match_player21$player_fifa_api_id.y=NULL
#AP11
match_player22 <- merge(x = match_player21, y=player_atts,by.x='away_player_11',by.y='player_api_id',all.x=TRUE)
match_player22$date.x<-ymd(match_player22$date.x)
match_player22$date<-ymd_hms(match_player22$date)
match_player22$time_diff <- difftime(match_player22$date.x, match_player22$date,units='days')
match_player22 = match_player22[match_player22$time_diff >= 0,]
match_player22 = match_player22 %>%
  group_by(match_api_id, away_player_11) %>%
  filter(time_diff == min(time_diff))
for (i in 858:895){
  colnames(match_player22)[i] = paste(colnames(match_player22)[i], "aw_p_11", sep = "_")
}
for (i in 858:895){
  match_player22[[i]] = paste(match_player22[[i]],match_player22[[56]],sep="_")
}
match_player22$time_diff=NULL
match_player22$id.y = NULL
match_player22$date.y=NULL
match_player22$date=NULL
match_player22$id.x=NULL
match_player22$id=NULL
match_player22$player_fifa_api_id.x=NULL
match_player22$player_fifa_api_id.y=NULL
```
  
  
  In the final dataset, each cell contains position, attribute and its value
Finally, we create unique item composed of position, player attribute and attribute value so that when we run association rule, the we can identify the attributes needed for different posisitions. We added the position and attribute name into its value as prefix, and then deleted the player number since we only care about the position layout we need to win against Juventus.

```{r, message=FALSE}
options(warn=-1)
match_trans = match_player22

### Juventus plays as home team, need to use away player attributes in the next steps
home_match_trans = match_trans[match_trans$opponent == match_trans$away_team_api_id,]
home_trans_ar = home_match_trans %>%
  select(preferred_foot_aw_p_1:gk_reflexes_Bucket_aw_p_11, result)
home_trans_ar = home_trans_ar[,-c(1,2)]
home_trans_ar = subset(home_trans_ar, select = -player_fifa_api_id)

### Juventus plays as away team, need to use home player attributes in the next steps
away_match_trans = match_trans[match_trans$opponent == match_trans$home_team_api_id,]
away_trans_ar = away_match_trans %>%
  select(preferred_foot_hp_1:gk_reflexes_Bucket_hp_11, result)
away_trans_ar = away_trans_ar[,-c(1,2)]

colnames(away_trans_ar) = colnames(home_trans_ar)
all_trans_ar = rbind(home_trans_ar, away_trans_ar)

##### add column name to values
column_names = names(all_trans_ar)
for (column in column_names) {
  all_trans_ar[[column]] = paste(column, all_trans_ar[[column]], sep = '_')
}

###### delete player numbers
for (i in 1:418) {
  for (j in 1:287) {
    all_trans_ar[j,i] = gsub('_aw_p_[0-9]', '', all_trans_ar[j,i])
  }
}
for (i in 1:418) {
  for (j in 1:287) {
    all_trans_ar[j,i] = gsub('[0-9]', '', all_trans_ar[j,i])
  }
}

#### write as final transaction data
write.csv(all_trans_ar,'juventus.csv')
#head(all_trans_ar)
```

## Findings and Recommendations
While aiming for the maximum points, we want to have a set of players that give us winning results. Utilizing results from the association rules analysis relating to our opponents' losses.
This way, we set up our team to perform better against the opponents we typically lose the most. 

Based on our findings from the association analysis for each of our top opponents,we recommend strategies to field players with specific attributes and abilities for different areas of the field.

##### Juventus

```{r, results = "hide", message = F, warning = F}

juventus_all = read.transactions("juventus.csv", format = "basket",
                           sep = ",", rm.duplicates = TRUE, skip = 1, header = F)
# inspect(juventus)
# itemInfo(juventus)
rules <- apriori(juventus_all, parameter = list(supp = 0.1, conf = 0.34), 
                 appearance = list(rhs = 'result_loss'))

rules_lift = sort(rules,by='lift',decreasing = TRUE)
```
  
  When we run the associations of player attributes that correspond to Juventus's loss, we found the following rules:

```{r, fig.width=16}
inspect(rules_lift[1:10])
```
  
  Plotting on a parallel coordinaltes plot helps to visualize the most important player attributes.

```{r}
# plot(rules_lift[1:5], method = 'graph', engine = 'htmlwidget')
plot(rules_lift[1:10], method = 'paracoord')
```

##### Recommendations against Juventus

If we set up a team with fast forwards and defenders who can have the vision to spot a forward's run, we can get the better of Juventus

Another approach would be to have a mid-field with players can shoot and finish well. In this case, we don't need defenders with high vision. 


#### Sampdoria 

```{r, include = FALSE}
player_atts = player_atts_tbl %>% 
  collect()
long_team_name <- 'Sampdoria'
roma_record <- team_tbl %>% 
  collect() %>%
  filter(grepl(long_team_name, team_long_name))
home_matches <- match %>%
  filter(home_team_api_id == roma_record$team_api_id) %>%
  mutate(goal_diff = home_team_goal - away_team_goal) %>%
  mutate(type = 'home', opponent = away_team_api_id)
# hist(home_matches$goal_diff)
# summary(home_matches$goal_diff)

away_matches <- match %>%
  filter(away_team_api_id == roma_record$team_api_id) %>%
  mutate(goal_diff =away_team_goal - home_team_goal) %>%
  mutate(type = 'away', opponent = home_team_api_id)

# hist(away_matches$goal_diff)
# summary(away_matches$goal_diff)

all_match = rbind(home_matches, away_matches)
# ggplot(all_match, aes(type, goal_diff, col = type)) +
#   geom_boxplot()

all_match$result = as.numeric(all_match$goal_diff)
all_match[all_match$goal_diff > 0, ]$result = 'win'
all_match[all_match$goal_diff < 0, ]$result = 'loss'
all_match[all_match$goal_diff == 0, ]$result = 'draw'
# ggplot(all_match, aes(result)) +
#   geom_bar()

# ggplot(all_match[all_match$result == 'lose',], aes(as.factor(opponent))) +
#   geom_bar()

##################### position ###################
for (i in 1:11){
  x = paste("home_player_X",i,sep='')
  y = paste("home_player_Y",i,sep='')
  inp = paste("hm_ply_pos",i,sep="_")
  all_match[inp] = ifelse(all_match[x]==1 & all_match[y]==1,"Goaly",
                      ifelse(all_match[y]>=2 & all_match[y]<=5,"Defender",
                             ifelse(all_match[y]>=6 & all_match[y]<=8,"Mid Fielders",
                                    ifelse(all_match[y]>=9 & all_match[y]<=11,"Forwards","NA"))))
}

for (i in 1:11){
  x = paste("away_player_X",i,sep='')
  y = paste("away_player_Y",i,sep='')
  inp = paste("away_ply_pos",i,sep="_")
  all_match[inp] = ifelse(all_match[x]==1 & all_match[y]==1,"Goaly",
                      ifelse(all_match[y]>=2 & all_match[y]<=5,"Defender",
                             ifelse(all_match[y]>=6 & all_match[y]<=8,"Mid Fielders",
                                    ifelse(all_match[y]>=9 & all_match[y]<=11,"Forwards","NA"))))
}
```

```{r, include  = FALSE, message=FALSE, results="hide"}
column_names = c("overall_rating","potential","crossing", "finishing","heading_accuracy",    
                 "short_passing", "volleys","dribbling",    
                 "curve", "free_kick_accuracy" ,"long_passing",    
                 "ball_control","acceleration","sprint_speed",    
                 "agility","reactions","balance",    
                 "shot_power","jumping","stamina",    
                 "strength","long_shots","aggression",    
                 "interceptions","positioning","vision",    
                 "penalties", "marking","standing_tackle",
                 "sliding_tackle","gk_diving","gk_handling",    
                 "gk_kicking","gk_positioning","gk_reflexes")

for (i in column_names){
  k = paste(i, "Bucket",sep="_")
  player_atts[k] = 
    cut(player_atts[[i]], breaks = 5, labels=c('low','low-med','med','med-high','high'))
}

player_atts <- select(player_atts, c(1:9, overall_rating_Bucket:gk_reflexes_Bucket))
player_atts = player_atts[, -c(5,6)]
all_match <- select(all_match, c(id:away_team_goal, home_player_1:away_player_11, opponent:away_ply_pos_11))

#######
# match_g <- gather(all_match, player, player_id, home_player_1:away_player_11, na.rm = TRUE)
# View(match_g)
# match_s <- arrange(match_g, match_api_id, player)
# View(match_s)
# #match_s <- select(match_s, c(1:10, player, player_id))

# colnames(match_s)[37] <- "player_api_id"

#HP1
match_player <- merge(x = all_match, y=player_atts,by.x='home_player_1',by.y='player_api_id',all.x=TRUE)
match_player$date.x<-ymd_hms(match_player$date.x)
match_player$date.y<-ymd_hms(match_player$date.y)
match_player$time_diff <- difftime(match_player$date.x, match_player$date.y,units='days')
match_player = match_player[match_player$time_diff >= 0,]
match_player_1 = match_player %>%
  group_by(match_api_id, home_player_1) %>%
  filter(time_diff == min(time_diff))
for (i in 61:98){
  colnames(match_player_1)[i] = paste(colnames(match_player_1)[i], "hp_1", sep = "_")
}
for (i in 61:98){
  match_player_1[[i]] = paste(match_player_1[[i]],match_player_1[[36]],sep="_")
}
match_player_1$time_diff=NULL
# HP2

match_player2 <- merge(x = match_player_1, y=player_atts,by.x='home_player_2',by.y='player_api_id',all.x=TRUE)
match_player2$date.x<-ymd(match_player2$date.x)
match_player2$date<-ymd_hms(match_player2$date)
match_player2$time_diff <- difftime(match_player2$date.x, match_player2$date,units='days')
match_player2 = match_player2[match_player2$time_diff >= 0,]
match_player2 = match_player2 %>%
  group_by(match_api_id, home_player_2) %>%
  filter(time_diff == min(time_diff))
for (i in 102:139){
  colnames(match_player2)[i] = paste(colnames(match_player2)[i], "hp_2", sep = "_")
}
for (i in 102:139){
  match_player2[[i]] = paste(match_player2[[i]],match_player2[[37]],sep="_")
}
match_player2$time_diff=NULL
match_player2$id.y = NULL
match_player2$date.y=NULL
match_player2$date=NULL
match_player2$id.x=NULL
##
#HP3

match_player3 <- merge(x = match_player2, y=player_atts,by.x='home_player_3',by.y='player_api_id',all.x=TRUE)
match_player3$date.x<-ymd(match_player3$date.x)
match_player3$date<-ymd_hms(match_player3$date)
match_player3$time_diff <- difftime(match_player3$date.x, match_player3$date,units='days')
match_player3 = match_player3[match_player3$time_diff >= 0,]
match_player3 = match_player3 %>%
  group_by(match_api_id, home_player_3) %>%
  filter(time_diff == min(time_diff))
for (i in 139:176){
  colnames(match_player3)[i] = paste(colnames(match_player3)[i], "hp_3", sep = "_")
}
for (i in 139:176){
  match_player3[[i]] = paste(match_player3[[i]],match_player3[[37]],sep="_")
}
match_player3$time_diff=NULL
match_player3$id.y = NULL
match_player3$date.y=NULL
match_player3$date=NULL
match_player3$id.x=NULL
match_player3$player_fifa_api_id=NULL

#HP4

match_player4 <- merge(x = match_player3, y=player_atts,by.x='home_player_4',by.y='player_api_id',all.x=TRUE)
match_player4$date.x<-ymd(match_player4$date.x)
match_player4$date<-ymd_hms(match_player4$date)
match_player4$time_diff <- difftime(match_player4$date.x, match_player4$date,units='days')
match_player4 = match_player4[match_player4$time_diff >= 0,]
match_player4 = match_player4 %>%
  group_by(match_api_id, home_player_4) %>%
  filter(time_diff == min(time_diff))
for (i in 176:213){
  colnames(match_player4)[i] = paste(colnames(match_player4)[i], "hp_4", sep = "_")
}
for (i in 176:213){
  match_player4[[i]] = paste(match_player4[[i]],match_player4[[38]],sep="_")
}
match_player4$time_diff=NULL
match_player4$id.y = NULL
match_player4$date.y=NULL
match_player4$date=NULL
match_player4$id.x=NULL
match_player4$id=NULL
match_player4$player_fifa_api_id.x=NULL
match_player4$player_fifa_api_id.y=NULL
#HP5

match_player5 <- merge(x = match_player4, y=player_atts,by.x='home_player_5',by.y='player_api_id',all.x=TRUE)
match_player5$date.x<-ymd(match_player5$date.x)
match_player5$date<-ymd_hms(match_player5$date)
match_player5$time_diff <- difftime(match_player5$date.x, match_player5$date,units='days')
match_player5 = match_player5[match_player5$time_diff >= 0,]
match_player5 = match_player5 %>%
  group_by(match_api_id, home_player_5) %>%
  filter(time_diff == min(time_diff))
for (i in 213:250){
  colnames(match_player5)[i] = paste(colnames(match_player5)[i], "hp_5", sep = "_")
}
for (i in 213:250){
  match_player5[[i]] = paste(match_player5[[i]],match_player5[[39]],sep="_")
}
match_player5$time_diff=NULL
match_player5$id.y = NULL
match_player5$date.y=NULL
match_player5$date=NULL
match_player5$id.x=NULL
match_player5$id=NULL
###
#HP6
match_player6 <- merge(x = match_player5, y=player_atts,by.x='home_player_6',by.y='player_api_id',all.x=TRUE)
match_player6$date.x<-ymd(match_player6$date.x)
match_player6$date<-ymd_hms(match_player6$date)
match_player6$time_diff <- difftime(match_player6$date.x, match_player6$date,units='days')
match_player6 = match_player6[match_player6$time_diff >= 0,]
match_player6 = match_player6 %>%
  group_by(match_api_id, home_player_6) %>%
  filter(time_diff == min(time_diff))
for (i in 252:289){
  colnames(match_player6)[i] = paste(colnames(match_player6)[i], "hp_6", sep = "_")
}
for (i in 252:289){
  match_player6[[i]] = paste(match_player6[[i]],match_player6[[40]],sep="_")
}
match_player6$time_diff=NULL
match_player6$id.y = NULL
match_player6$date.y=NULL
match_player6$date=NULL
match_player6$id.x=NULL
match_player6$id=NULL
match_player6$player_fifa_api_id.x=NULL
match_player6$player_fifa_api_id.y=NULL

#HP7
match_player7 <- merge(x = match_player6, y=player_atts,by.x='home_player_7',by.y='player_api_id',all.x=TRUE)
match_player7$date.x<-ymd(match_player7$date.x)
match_player7$date<-ymd_hms(match_player7$date)
match_player7$time_diff <- difftime(match_player7$date.x, match_player7$date,units='days')
match_player7 = match_player7[match_player7$time_diff >= 0,]
match_player7 = match_player7 %>%
  group_by(match_api_id, home_player_7) %>%
  filter(time_diff == min(time_diff))
for (i in 289:326){
  colnames(match_player7)[i] = paste(colnames(match_player7)[i], "hp_7", sep = "_")
}
for (i in 289:326){
  match_player7[[i]] = paste(match_player7[[i]],match_player7[[41]],sep="_")
}
match_player7$time_diff=NULL
match_player7$id.y = NULL
match_player7$date.y=NULL
match_player7$date=NULL
match_player7$id.x=NULL
match_player7$id=NULL
match_player7$player_fifa_api_id.x=NULL
match_player7$player_fifa_api_id.y=NULL

#HP8
match_player8 <- merge(x = match_player7, y=player_atts,by.x='home_player_8',by.y='player_api_id',all.x=TRUE)
match_player8$date.x<-ymd(match_player8$date.x)
match_player8$date<-ymd_hms(match_player8$date)
match_player8$time_diff <- difftime(match_player8$date.x, match_player8$date,units='days')
match_player8 = match_player8[match_player8$time_diff >= 0,]
match_player8 = match_player8 %>%
  group_by(match_api_id, home_player_8) %>%
  filter(time_diff == min(time_diff))
for (i in 326:363){
  colnames(match_player8)[i] = paste(colnames(match_player8)[i], "hp_8", sep = "_")
}
for (i in 326:363){
  match_player8[[i]] = paste(match_player8[[i]],match_player8[[42]],sep="_")
}
match_player8$time_diff=NULL
match_player8$id.y = NULL
match_player8$date.y=NULL
match_player8$date=NULL
match_player8$id.x=NULL
match_player8$id=NULL
match_player8$player_fifa_api_id.x=NULL
match_player8$player_fifa_api_id.y=NULL

#HP9
match_player9 <- merge(x = match_player8, y=player_atts,by.x='home_player_9',by.y='player_api_id',all.x=TRUE)
match_player9$date.x<-ymd(match_player9$date.x)
match_player9$date<-ymd_hms(match_player9$date)
match_player9$time_diff <- difftime(match_player9$date.x, match_player9$date,units='days')
match_player9 = match_player9[match_player9$time_diff >= 0,]
match_player9 = match_player9 %>%
  group_by(match_api_id, home_player_9) %>%
  filter(time_diff == min(time_diff))
for (i in 365:402){
  colnames(match_player9)[i] = paste(colnames(match_player9)[i], "hp_9", sep = "_")
}
for (i in 365:402){
  match_player9[[i]] = paste(match_player9[[i]],match_player9[[43]],sep="_")
}
match_player9$time_diff=NULL
match_player9$id.y = NULL
match_player9$date.y=NULL
match_player9$date=NULL
match_player9$id.x=NULL
match_player9$id=NULL
match_player9$player_fifa_api_id.x=NULL
match_player9$player_fifa_api_id.y=NULL

#HP10
match_player10 <- merge(x = match_player9, y=player_atts,by.x='home_player_10',by.y='player_api_id',all.x=TRUE)
match_player10$date.x<-ymd(match_player10$date.x)
match_player10$date<-ymd_hms(match_player10$date)
match_player10$time_diff <- difftime(match_player10$date.x, match_player10$date,units='days')
match_player10 = match_player10[match_player10$time_diff >= 0,]
match_player10 = match_player10 %>%
  group_by(match_api_id, home_player_10) %>%
  filter(time_diff == min(time_diff))
for (i in 402:439){
  colnames(match_player10)[i] = paste(colnames(match_player10)[i], "hp_10", sep = "_")
}
for (i in 402:439){
  match_player10[[i]] = paste(match_player10[[i]],match_player10[[44]],sep="_")
}
match_player10$time_diff=NULL
match_player10$id.y = NULL
match_player10$date.y=NULL
match_player10$date=NULL
match_player10$id.x=NULL
match_player10$id=NULL
match_player10$player_fifa_api_id.x=NULL
match_player10$player_fifa_api_id.y=NULL

#HP11
match_player11 <- merge(x = match_player10, y=player_atts,by.x='home_player_11',by.y='player_api_id',all.x=TRUE)
match_player11$date.x<-ymd(match_player11$date.x)
match_player11$date<-ymd_hms(match_player11$date)
match_player11$time_diff <- difftime(match_player11$date.x, match_player11$date,units='days')
match_player11 = match_player11[match_player11$time_diff >= 0,]
match_player11 = match_player11 %>%
  group_by(match_api_id, home_player_11) %>%
  filter(time_diff == min(time_diff))
for (i in 441:478){
  colnames(match_player11)[i] = paste(colnames(match_player11)[i], "hp_11", sep = "_")
}
for (i in 441:478){
  match_player11[[i]] = paste(match_player11[[i]],match_player11[[45]],sep="_")
}
match_player11$time_diff=NULL
match_player11$id.y = NULL
match_player11$date.y=NULL
match_player11$date=NULL
match_player11$id.x=NULL
match_player11$id=NULL
match_player11$player_fifa_api_id.x=NULL
match_player11$player_fifa_api_id.y=NULL

#AP1

match_player12 <- merge(x = match_player11, y=player_atts,by.x='away_player_1',by.y='player_api_id',all.x=TRUE)
match_player12$date.x<-ymd(match_player12$date.x)
match_player12$date<-ymd_hms(match_player12$date)
match_player12$time_diff <- difftime(match_player12$date.x, match_player12$date,units='days')
match_player12 = match_player12[match_player12$time_diff >= 0,]
match_player12 = match_player12 %>%
  group_by(match_api_id, away_player_1) %>%
  filter(time_diff == min(time_diff))
for (i in 478:515){
  colnames(match_player12)[i] = paste(colnames(match_player12)[i], "aw_p_1", sep = "_")
}
for (i in 478:515){
  match_player12[[i]] = paste(match_player12[[i]],match_player12[[46]],sep="_")
}
match_player12$time_diff=NULL
match_player12$id.y = NULL
match_player12$date.y=NULL
match_player12$date=NULL
match_player12$id.x=NULL
match_player12$id=NULL
match_player12$player_fifa_api_id.x=NULL
match_player12$player_fifa_api_id.y=NULL
#AP2
match_player13 <- merge(x = match_player12, y=player_atts,by.x='away_player_2',by.y='player_api_id',all.x=TRUE)
match_player13$date.x<-ymd(match_player13$date.x)
match_player13$date<-ymd_hms(match_player13$date)
match_player13$time_diff <- difftime(match_player13$date.x, match_player13$date,units='days')
match_player13 = match_player13[match_player13$time_diff >= 0,]
match_player13 = match_player13 %>%
  group_by(match_api_id, away_player_2) %>%
  filter(time_diff == min(time_diff))
for (i in 517:554){
  colnames(match_player13)[i] = paste(colnames(match_player13)[i], "aw_p_2", sep = "_")
}
for (i in 517:554){
  match_player13[[i]] = paste(match_player13[[i]],match_player13[[47]],sep="_")
}
match_player13$time_diff=NULL
match_player13$id.y = NULL
match_player13$date.y=NULL
match_player13$date=NULL
match_player13$id.x=NULL
match_player13$id=NULL
match_player13$player_fifa_api_id.x=NULL
match_player13$player_fifa_api_id.y=NULL

#AP3
match_player14 <- merge(x = match_player13, y=player_atts,by.x='away_player_3',by.y='player_api_id',all.x=TRUE)
match_player14$date.x<-ymd(match_player14$date.x)
match_player14$date<-ymd_hms(match_player14$date)
match_player14$time_diff <- difftime(match_player14$date.x, match_player14$date,units='days')
match_player14 = match_player14[match_player14$time_diff >= 0,]
match_player14 = match_player14 %>%
  group_by(match_api_id, away_player_3) %>%
  filter(time_diff == min(time_diff))
for (i in 554:591){
  colnames(match_player14)[i] = paste(colnames(match_player14)[i], "aw_p_3", sep = "_")
}
for (i in 554:591){
  match_player14[[i]] = paste(match_player14[[i]],match_player14[[48]],sep="_")
}
match_player14$time_diff=NULL
match_player14$id.y = NULL
match_player14$date.y=NULL
match_player14$date=NULL
match_player14$id.x=NULL
match_player14$id=NULL
match_player14$player_fifa_api_id.x=NULL
match_player14$player_fifa_api_id.y=NULL

#AP4
match_player15 <- merge(x = match_player14, y=player_atts,by.x='away_player_4',by.y='player_api_id',all.x=TRUE)
match_player15$date.x<-ymd(match_player15$date.x)
match_player15$date<-ymd_hms(match_player15$date)
match_player15$time_diff <- difftime(match_player15$date.x, match_player15$date,units='days')
match_player15 = match_player15[match_player15$time_diff >= 0,]
match_player15 = match_player15 %>%
  group_by(match_api_id, away_player_4) %>%
  filter(time_diff == min(time_diff))
for (i in 593:630){
  colnames(match_player15)[i] = paste(colnames(match_player15)[i], "aw_p_4", sep = "_")
}
for (i in 593:630){
  match_player15[[i]] = paste(match_player15[[i]],match_player15[[49]],sep="_")
}
match_player15$time_diff=NULL
match_player15$id.y = NULL
match_player15$date.y=NULL
match_player15$date=NULL
match_player15$id.x=NULL
match_player15$id=NULL
match_player15$player_fifa_api_id.x=NULL
match_player15$player_fifa_api_id.y=NULL

#AP5
match_player16 <- merge(x = match_player15, y=player_atts,by.x='away_player_5',by.y='player_api_id',all.x=TRUE)
match_player16$date.x<-ymd(match_player16$date.x)
match_player16$date<-ymd_hms(match_player16$date)
match_player16$time_diff <- difftime(match_player16$date.x, match_player16$date,units='days')
match_player16 = match_player16[match_player16$time_diff >= 0,]
match_player16 = match_player16 %>%
  group_by(match_api_id, away_player_5) %>%
  filter(time_diff == min(time_diff))
for (i in 630:667){
  colnames(match_player16)[i] = paste(colnames(match_player16)[i], "aw_p_5", sep = "_")
}
for (i in 630:667){
  match_player16[[i]] = paste(match_player16[[i]],match_player16[[50]],sep="_")
}
match_player16$time_diff=NULL
match_player16$id.y = NULL
match_player16$date.y=NULL
match_player16$date=NULL
match_player16$id.x=NULL
match_player16$id=NULL
match_player16$player_fifa_api_id.x=NULL
match_player16$player_fifa_api_id.y=NULL
#AP6
match_player17 <- merge(x = match_player16, y=player_atts,by.x='away_player_6',by.y='player_api_id',all.x=TRUE)
match_player17$date.x<-ymd(match_player17$date.x)
match_player17$date<-ymd_hms(match_player17$date)
match_player17$time_diff <- difftime(match_player17$date.x, match_player17$date,units='days')
match_player17 = match_player17[match_player17$time_diff >= 0,]
match_player17 = match_player17 %>%
  group_by(match_api_id, away_player_6) %>%
  filter(time_diff == min(time_diff))
for (i in 669:706){
  colnames(match_player17)[i] = paste(colnames(match_player17)[i], "aw_p_6", sep = "_")
}
for (i in 669:706){
  match_player17[[i]] = paste(match_player17[[i]],match_player17[[51]],sep="_")
}
match_player17$time_diff=NULL
match_player17$id.y = NULL
match_player17$date.y=NULL
match_player17$date=NULL
match_player17$id.x=NULL
match_player17$id=NULL
match_player17$player_fifa_api_id.x=NULL
match_player17$player_fifa_api_id.y=NULL
#AP7
match_player18 <- merge(x = match_player17, y=player_atts,by.x='away_player_7',by.y='player_api_id',all.x=TRUE)
match_player18$date.x<-ymd(match_player18$date.x)
match_player18$date<-ymd_hms(match_player18$date)
match_player18$time_diff <- difftime(match_player18$date.x, match_player18$date,units='days')
match_player18 = match_player18[match_player18$time_diff >= 0,]
match_player18 = match_player18 %>%
  group_by(match_api_id, away_player_7) %>%
  filter(time_diff == min(time_diff))
for (i in 706:743){
  colnames(match_player18)[i] = paste(colnames(match_player18)[i], "aw_p_7", sep = "_")
}
for (i in 706:743){
  match_player18[[i]] = paste(match_player18[[i]],match_player18[[52]],sep="_")
}
match_player18$time_diff=NULL
match_player18$id.y = NULL
match_player18$date.y=NULL
match_player18$date=NULL
match_player18$id.x=NULL
match_player18$id=NULL
match_player18$player_fifa_api_id.x=NULL
match_player18$player_fifa_api_id.y=NULL
#AP8
match_player19 <- merge(x = match_player18, y=player_atts,by.x='away_player_8',by.y='player_api_id',all.x=TRUE)
match_player19$date.x<-ymd(match_player19$date.x)
match_player19$date<-ymd_hms(match_player19$date)
match_player19$time_diff <- difftime(match_player19$date.x, match_player19$date,units='days')
match_player19 = match_player19[match_player19$time_diff >= 0,]
match_player19 = match_player19 %>%
  group_by(match_api_id, away_player_8) %>%
  filter(time_diff == min(time_diff))
for (i in 745:782){
  colnames(match_player19)[i] = paste(colnames(match_player19)[i], "aw_p_8", sep = "_")
}
for (i in 745:782){
  match_player19[[i]] = paste(match_player19[[i]],match_player19[[53]],sep="_")
}
match_player19$time_diff=NULL
match_player19$id.y = NULL
match_player19$date.y=NULL
match_player19$date=NULL
match_player19$id.x=NULL
match_player19$id=NULL
match_player19$player_fifa_api_id.x=NULL
match_player19$player_fifa_api_id.y=NULL
#AP9
match_player20 <- merge(x = match_player19, y=player_atts,by.x='away_player_9',by.y='player_api_id',all.x=TRUE)
match_player20$date.x<-ymd(match_player20$date.x)
match_player20$date<-ymd_hms(match_player20$date)
match_player20$time_diff <- difftime(match_player20$date.x, match_player20$date,units='days')
match_player20 = match_player20[match_player20$time_diff >= 0,]
match_player20 = match_player20 %>%
  group_by(match_api_id, away_player_9) %>%
  filter(time_diff == min(time_diff))
for (i in 782:819){
  colnames(match_player20)[i] = paste(colnames(match_player20)[i], "aw_p_9", sep = "_")
}
for (i in 782:819){
  match_player20[[i]] = paste(match_player20[[i]],match_player20[[54]],sep="_")
}
match_player20$time_diff=NULL
match_player20$id.y = NULL
match_player20$date.y=NULL
match_player20$date=NULL
match_player20$id.x=NULL
match_player20$id=NULL
match_player20$player_fifa_api_id.x=NULL
match_player20$player_fifa_api_id.y=NULL
#AP10
match_player21 <- merge(x = match_player20, y=player_atts,by.x='away_player_10',by.y='player_api_id',all.x=TRUE)
match_player21$date.x<-ymd(match_player21$date.x)
match_player21$date<-ymd_hms(match_player21$date)
match_player21$time_diff <- difftime(match_player21$date.x, match_player21$date,units='days')
match_player21 = match_player21[match_player21$time_diff >= 0,]
match_player21 = match_player21 %>%
  group_by(match_api_id, away_player_10) %>%
  filter(time_diff == min(time_diff))
for (i in 821:858){
  colnames(match_player21)[i] = paste(colnames(match_player21)[i], "aw_p_10", sep = "_")
}
for (i in 821:858){
  match_player21[[i]] = paste(match_player21[[i]],match_player21[[55]],sep="_")
}
match_player21$time_diff=NULL
match_player21$id.y = NULL
match_player21$date.y=NULL
match_player21$date=NULL
match_player21$id.x=NULL
match_player21$id=NULL
match_player21$player_fifa_api_id.x=NULL
match_player21$player_fifa_api_id.y=NULL
#AP11
match_player22 <- merge(x = match_player21, y=player_atts,by.x='away_player_11',by.y='player_api_id',all.x=TRUE)
match_player22$date.x<-ymd(match_player22$date.x)
match_player22$date<-ymd_hms(match_player22$date)
match_player22$time_diff <- difftime(match_player22$date.x, match_player22$date,units='days')
match_player22 = match_player22[match_player22$time_diff >= 0,]
match_player22 = match_player22 %>%
  group_by(match_api_id, away_player_11) %>%
  filter(time_diff == min(time_diff))
for (i in 858:895){
  colnames(match_player22)[i] = paste(colnames(match_player22)[i], "aw_p_11", sep = "_")
}
for (i in 858:895){
  match_player22[[i]] = paste(match_player22[[i]],match_player22[[56]],sep="_")
}
match_player22$time_diff=NULL
match_player22$id.y = NULL
match_player22$date.y=NULL
match_player22$date=NULL
match_player22$id.x=NULL
match_player22$id=NULL
match_player22$player_fifa_api_id.x=NULL
match_player22$player_fifa_api_id.y=NULL

################# ARules ##################
# all the matches that lose
loss_match = match_player22
### lose as home play, need to use away player attributes in the next steps
home_loss_match = loss_match[loss_match$opponent == loss_match$away_team_api_id,]
home_loss_ar = home_loss_match %>%
  select(preferred_foot_aw_p_1:gk_reflexes_Bucket_aw_p_11, result)
home_loss_ar = home_loss_ar[,-c(1,2)]
home_loss_ar = subset(home_loss_ar, select = -player_fifa_api_id)
### lose as away play, need to use home player attributes in the next steps
away_loss_match = loss_match[loss_match$opponent == loss_match$home_team_api_id,]
away_loss_ar = away_loss_match %>%
  select(preferred_foot_hp_1:gk_reflexes_Bucket_hp_11, result)
away_loss_ar = away_loss_ar[,-c(1,2)]
colnames(away_loss_ar) = colnames(home_loss_ar)
all_loss_ar = rbind(home_loss_ar, away_loss_ar)
##### add column name to values
column_names = names(all_loss_ar)

for (column in column_names) {
  all_loss_ar[[column]] = paste(column, all_loss_ar[[column]], sep = '_')
}

###### delete player numbers
for (i in 1:418) {
  for (j in 1:287) {
    all_loss_ar[j,i] = gsub('_aw_p_[0-9]', '', all_loss_ar[j,i])
  }
}
for (i in 1:418) {
  for (j in 1:287) {
    all_loss_ar[j,i] = gsub('[0-9]', '', all_loss_ar[j,i])
  }
}


write.csv(all_loss_ar,'sampdoria.csv')
```

```{r include = FALSE}
sampdoria_all3 = read.transactions("sampdoria.csv", format = "basket",
                           sep = ",", rm.duplicates = TRUE, skip = 1, header = FALSE)
# inspect(sampdoria_all3)
# itemInfo(sampdoria_all3)
rules <- apriori(sampdoria_all3, parameter = list(supp = 0.2, conf = 0.3), appearance = list(rhs = 'result_loss'))

rules_lift = sort(rules,by='lift',decreasing = TRUE)
```

 When we run the associations of player attributes that correspond to Sampdoria's loss, we found the following rules:

```{r, fig.width=16}
inspect(rules_lift[1:10])
```

```{r}
# plot(rules_lift[1:5], method = 'graph', engine = 'htmlwidget')
plot(rules_lift[1:10], method = 'paracoord')
```

##### Recommendations against Sampdoria

The best way to setup against Sampdoria is to include box to box mid-fielders with high stamina. These will help turn defense to attack in games. They can be set with forwards with high finishing and volleying skills to make the most of the attacking move


#### Palermo

```{r, include = FALSE}
player_atts = player_atts_tbl %>% 
  collect()
long_team_name <- 'Palermo'
roma_record <- team_tbl %>% 
  collect() %>%
  filter(grepl(long_team_name, team_long_name))
home_matches <- match %>%
  filter(home_team_api_id == roma_record$team_api_id) %>%
  mutate(goal_diff = home_team_goal - away_team_goal) %>%
  mutate(type = 'home', opponent = away_team_api_id)
# hist(home_matches$goal_diff)
# summary(home_matches$goal_diff)

away_matches <- match %>%
  filter(away_team_api_id == roma_record$team_api_id) %>%
  mutate(goal_diff =away_team_goal - home_team_goal) %>%
  mutate(type = 'away', opponent = home_team_api_id)

# hist(away_matches$goal_diff)
# summary(away_matches$goal_diff)

all_match = rbind(home_matches, away_matches)
# ggplot(all_match, aes(type, goal_diff, col = type)) +
#   geom_boxplot()

all_match$result = as.numeric(all_match$goal_diff)
all_match[all_match$goal_diff > 0, ]$result = 'win'
all_match[all_match$goal_diff < 0, ]$result = 'loss'
all_match[all_match$goal_diff == 0, ]$result = 'draw'
# ggplot(all_match, aes(result)) +
#   geom_bar()

# ggplot(all_match[all_match$result == 'lose',], aes(as.factor(opponent))) +
#   geom_bar()

##################### position ###################
for (i in 1:11){
  x = paste("home_player_X",i,sep='')
  y = paste("home_player_Y",i,sep='')
  inp = paste("hm_ply_pos",i,sep="_")
  all_match[inp] = ifelse(all_match[x]==1 & all_match[y]==1,"Goaly",
                      ifelse(all_match[y]>=2 & all_match[y]<=5,"Defender",
                             ifelse(all_match[y]>=6 & all_match[y]<=8,"Mid Fielders",
                                    ifelse(all_match[y]>=9 & all_match[y]<=11,"Forwards","NA"))))
}

for (i in 1:11){
  x = paste("away_player_X",i,sep='')
  y = paste("away_player_Y",i,sep='')
  inp = paste("away_ply_pos",i,sep="_")
  all_match[inp] = ifelse(all_match[x]==1 & all_match[y]==1,"Goaly",
                      ifelse(all_match[y]>=2 & all_match[y]<=5,"Defender",
                             ifelse(all_match[y]>=6 & all_match[y]<=8,"Mid Fielders",
                                    ifelse(all_match[y]>=9 & all_match[y]<=11,"Forwards","NA"))))
}
```

```{r, include = FALSE, message= FALSE}
column_names = c("overall_rating","potential","crossing", "finishing","heading_accuracy",    
                 "short_passing", "volleys","dribbling",    
                 "curve", "free_kick_accuracy" ,"long_passing",    
                 "ball_control","acceleration","sprint_speed",    
                 "agility","reactions","balance",    
                 "shot_power","jumping","stamina",    
                 "strength","long_shots","aggression",    
                 "interceptions","positioning","vision",    
                 "penalties", "marking","standing_tackle",
                 "sliding_tackle","gk_diving","gk_handling",    
                 "gk_kicking","gk_positioning","gk_reflexes")

for (i in column_names){
  k = paste(i, "Bucket",sep="_")
  player_atts[k] = 
    cut(player_atts[[i]], breaks = 5, labels=c('low','low-med','med','med-high','high'))
}

player_atts <- select(player_atts, c(1:9, overall_rating_Bucket:gk_reflexes_Bucket))
player_atts = player_atts[, -c(5,6)]
all_match <- select(all_match, c(id:away_team_goal, home_player_1:away_player_11, opponent:away_ply_pos_11))

#######
# match_g <- gather(all_match, player, player_id, home_player_1:away_player_11, na.rm = TRUE)
# View(match_g)
# match_s <- arrange(match_g, match_api_id, player)
# View(match_s)
# #match_s <- select(match_s, c(1:10, player, player_id))

# colnames(match_s)[37] <- "player_api_id"

#HP1
match_player <- merge(x = all_match, y=player_atts,by.x='home_player_1',by.y='player_api_id',all.x=TRUE)
match_player$date.x<-ymd_hms(match_player$date.x)
match_player$date.y<-ymd_hms(match_player$date.y)
match_player$time_diff <- difftime(match_player$date.x, match_player$date.y,units='days')
match_player = match_player[match_player$time_diff >= 0,]
match_player_1 = match_player %>%
  group_by(match_api_id, home_player_1) %>%
  filter(time_diff == min(time_diff))
for (i in 61:98){
  colnames(match_player_1)[i] = paste(colnames(match_player_1)[i], "hp_1", sep = "_")
}
for (i in 61:98){
  match_player_1[[i]] = paste(match_player_1[[i]],match_player_1[[36]],sep="_")
}
match_player_1$time_diff=NULL
# HP2

match_player2 <- merge(x = match_player_1, y=player_atts,by.x='home_player_2',by.y='player_api_id',all.x=TRUE)
match_player2$date.x<-ymd(match_player2$date.x)
match_player2$date<-ymd_hms(match_player2$date)
match_player2$time_diff <- difftime(match_player2$date.x, match_player2$date,units='days')
match_player2 = match_player2[match_player2$time_diff >= 0,]
match_player2 = match_player2 %>%
  group_by(match_api_id, home_player_2) %>%
  filter(time_diff == min(time_diff))
for (i in 102:139){
  colnames(match_player2)[i] = paste(colnames(match_player2)[i], "hp_2", sep = "_")
}
for (i in 102:139){
  match_player2[[i]] = paste(match_player2[[i]],match_player2[[37]],sep="_")
}
match_player2$time_diff=NULL
match_player2$id.y = NULL
match_player2$date.y=NULL
match_player2$date=NULL
match_player2$id.x=NULL
##
#HP3

match_player3 <- merge(x = match_player2, y=player_atts,by.x='home_player_3',by.y='player_api_id',all.x=TRUE)
match_player3$date.x<-ymd(match_player3$date.x)
match_player3$date<-ymd_hms(match_player3$date)
match_player3$time_diff <- difftime(match_player3$date.x, match_player3$date,units='days')
match_player3 = match_player3[match_player3$time_diff >= 0,]
match_player3 = match_player3 %>%
  group_by(match_api_id, home_player_3) %>%
  filter(time_diff == min(time_diff))
for (i in 139:176){
  colnames(match_player3)[i] = paste(colnames(match_player3)[i], "hp_3", sep = "_")
}
for (i in 139:176){
  match_player3[[i]] = paste(match_player3[[i]],match_player3[[37]],sep="_")
}
match_player3$time_diff=NULL
match_player3$id.y = NULL
match_player3$date.y=NULL
match_player3$date=NULL
match_player3$id.x=NULL
match_player3$player_fifa_api_id=NULL

#HP4

match_player4 <- merge(x = match_player3, y=player_atts,by.x='home_player_4',by.y='player_api_id',all.x=TRUE)
match_player4$date.x<-ymd(match_player4$date.x)
match_player4$date<-ymd_hms(match_player4$date)
match_player4$time_diff <- difftime(match_player4$date.x, match_player4$date,units='days')
match_player4 = match_player4[match_player4$time_diff >= 0,]
match_player4 = match_player4 %>%
  group_by(match_api_id, home_player_4) %>%
  filter(time_diff == min(time_diff))
for (i in 176:213){
  colnames(match_player4)[i] = paste(colnames(match_player4)[i], "hp_4", sep = "_")
}
for (i in 176:213){
  match_player4[[i]] = paste(match_player4[[i]],match_player4[[38]],sep="_")
}
match_player4$time_diff=NULL
match_player4$id.y = NULL
match_player4$date.y=NULL
match_player4$date=NULL
match_player4$id.x=NULL
match_player4$id=NULL
match_player4$player_fifa_api_id.x=NULL
match_player4$player_fifa_api_id.y=NULL
#HP5

match_player5 <- merge(x = match_player4, y=player_atts,by.x='home_player_5',by.y='player_api_id',all.x=TRUE)
match_player5$date.x<-ymd(match_player5$date.x)
match_player5$date<-ymd_hms(match_player5$date)
match_player5$time_diff <- difftime(match_player5$date.x, match_player5$date,units='days')
match_player5 = match_player5[match_player5$time_diff >= 0,]
match_player5 = match_player5 %>%
  group_by(match_api_id, home_player_5) %>%
  filter(time_diff == min(time_diff))
for (i in 213:250){
  colnames(match_player5)[i] = paste(colnames(match_player5)[i], "hp_5", sep = "_")
}
for (i in 213:250){
  match_player5[[i]] = paste(match_player5[[i]],match_player5[[39]],sep="_")
}
match_player5$time_diff=NULL
match_player5$id.y = NULL
match_player5$date.y=NULL
match_player5$date=NULL
match_player5$id.x=NULL
match_player5$id=NULL
###
#HP6
match_player6 <- merge(x = match_player5, y=player_atts,by.x='home_player_6',by.y='player_api_id',all.x=TRUE)
match_player6$date.x<-ymd(match_player6$date.x)
match_player6$date<-ymd_hms(match_player6$date)
match_player6$time_diff <- difftime(match_player6$date.x, match_player6$date,units='days')
match_player6 = match_player6[match_player6$time_diff >= 0,]
match_player6 = match_player6 %>%
  group_by(match_api_id, home_player_6) %>%
  filter(time_diff == min(time_diff))
for (i in 252:289){
  colnames(match_player6)[i] = paste(colnames(match_player6)[i], "hp_6", sep = "_")
}
for (i in 252:289){
  match_player6[[i]] = paste(match_player6[[i]],match_player6[[40]],sep="_")
}
match_player6$time_diff=NULL
match_player6$id.y = NULL
match_player6$date.y=NULL
match_player6$date=NULL
match_player6$id.x=NULL
match_player6$id=NULL
match_player6$player_fifa_api_id.x=NULL
match_player6$player_fifa_api_id.y=NULL

#HP7
match_player7 <- merge(x = match_player6, y=player_atts,by.x='home_player_7',by.y='player_api_id',all.x=TRUE)
match_player7$date.x<-ymd(match_player7$date.x)
match_player7$date<-ymd_hms(match_player7$date)
match_player7$time_diff <- difftime(match_player7$date.x, match_player7$date,units='days')
match_player7 = match_player7[match_player7$time_diff >= 0,]
match_player7 = match_player7 %>%
  group_by(match_api_id, home_player_7) %>%
  filter(time_diff == min(time_diff))
for (i in 289:326){
  colnames(match_player7)[i] = paste(colnames(match_player7)[i], "hp_7", sep = "_")
}
for (i in 289:326){
  match_player7[[i]] = paste(match_player7[[i]],match_player7[[41]],sep="_")
}
match_player7$time_diff=NULL
match_player7$id.y = NULL
match_player7$date.y=NULL
match_player7$date=NULL
match_player7$id.x=NULL
match_player7$id=NULL
match_player7$player_fifa_api_id.x=NULL
match_player7$player_fifa_api_id.y=NULL

#HP8
match_player8 <- merge(x = match_player7, y=player_atts,by.x='home_player_8',by.y='player_api_id',all.x=TRUE)
match_player8$date.x<-ymd(match_player8$date.x)
match_player8$date<-ymd_hms(match_player8$date)
match_player8$time_diff <- difftime(match_player8$date.x, match_player8$date,units='days')
match_player8 = match_player8[match_player8$time_diff >= 0,]
match_player8 = match_player8 %>%
  group_by(match_api_id, home_player_8) %>%
  filter(time_diff == min(time_diff))
for (i in 326:363){
  colnames(match_player8)[i] = paste(colnames(match_player8)[i], "hp_8", sep = "_")
}
for (i in 326:363){
  match_player8[[i]] = paste(match_player8[[i]],match_player8[[42]],sep="_")
}
match_player8$time_diff=NULL
match_player8$id.y = NULL
match_player8$date.y=NULL
match_player8$date=NULL
match_player8$id.x=NULL
match_player8$id=NULL
match_player8$player_fifa_api_id.x=NULL
match_player8$player_fifa_api_id.y=NULL

#HP9
match_player9 <- merge(x = match_player8, y=player_atts,by.x='home_player_9',by.y='player_api_id',all.x=TRUE)
match_player9$date.x<-ymd(match_player9$date.x)
match_player9$date<-ymd_hms(match_player9$date)
match_player9$time_diff <- difftime(match_player9$date.x, match_player9$date,units='days')
match_player9 = match_player9[match_player9$time_diff >= 0,]
match_player9 = match_player9 %>%
  group_by(match_api_id, home_player_9) %>%
  filter(time_diff == min(time_diff))
for (i in 365:402){
  colnames(match_player9)[i] = paste(colnames(match_player9)[i], "hp_9", sep = "_")
}
for (i in 365:402){
  match_player9[[i]] = paste(match_player9[[i]],match_player9[[43]],sep="_")
}
match_player9$time_diff=NULL
match_player9$id.y = NULL
match_player9$date.y=NULL
match_player9$date=NULL
match_player9$id.x=NULL
match_player9$id=NULL
match_player9$player_fifa_api_id.x=NULL
match_player9$player_fifa_api_id.y=NULL

#HP10
match_player10 <- merge(x = match_player9, y=player_atts,by.x='home_player_10',by.y='player_api_id',all.x=TRUE)
match_player10$date.x<-ymd(match_player10$date.x)
match_player10$date<-ymd_hms(match_player10$date)
match_player10$time_diff <- difftime(match_player10$date.x, match_player10$date,units='days')
match_player10 = match_player10[match_player10$time_diff >= 0,]
match_player10 = match_player10 %>%
  group_by(match_api_id, home_player_10) %>%
  filter(time_diff == min(time_diff))
for (i in 402:439){
  colnames(match_player10)[i] = paste(colnames(match_player10)[i], "hp_10", sep = "_")
}
for (i in 402:439){
  match_player10[[i]] = paste(match_player10[[i]],match_player10[[44]],sep="_")
}
match_player10$time_diff=NULL
match_player10$id.y = NULL
match_player10$date.y=NULL
match_player10$date=NULL
match_player10$id.x=NULL
match_player10$id=NULL
match_player10$player_fifa_api_id.x=NULL
match_player10$player_fifa_api_id.y=NULL

#HP11
match_player11 <- merge(x = match_player10, y=player_atts,by.x='home_player_11',by.y='player_api_id',all.x=TRUE)
match_player11$date.x<-ymd(match_player11$date.x)
match_player11$date<-ymd_hms(match_player11$date)
match_player11$time_diff <- difftime(match_player11$date.x, match_player11$date,units='days')
match_player11 = match_player11[match_player11$time_diff >= 0,]
match_player11 = match_player11 %>%
  group_by(match_api_id, home_player_11) %>%
  filter(time_diff == min(time_diff))
for (i in 441:478){
  colnames(match_player11)[i] = paste(colnames(match_player11)[i], "hp_11", sep = "_")
}
for (i in 441:478){
  match_player11[[i]] = paste(match_player11[[i]],match_player11[[45]],sep="_")
}
match_player11$time_diff=NULL
match_player11$id.y = NULL
match_player11$date.y=NULL
match_player11$date=NULL
match_player11$id.x=NULL
match_player11$id=NULL
match_player11$player_fifa_api_id.x=NULL
match_player11$player_fifa_api_id.y=NULL

#AP1

match_player12 <- merge(x = match_player11, y=player_atts,by.x='away_player_1',by.y='player_api_id',all.x=TRUE)
match_player12$date.x<-ymd(match_player12$date.x)
match_player12$date<-ymd_hms(match_player12$date)
match_player12$time_diff <- difftime(match_player12$date.x, match_player12$date,units='days')
match_player12 = match_player12[match_player12$time_diff >= 0,]
match_player12 = match_player12 %>%
  group_by(match_api_id, away_player_1) %>%
  filter(time_diff == min(time_diff))
for (i in 478:515){
  colnames(match_player12)[i] = paste(colnames(match_player12)[i], "aw_p_1", sep = "_")
}
for (i in 478:515){
  match_player12[[i]] = paste(match_player12[[i]],match_player12[[46]],sep="_")
}
match_player12$time_diff=NULL
match_player12$id.y = NULL
match_player12$date.y=NULL
match_player12$date=NULL
match_player12$id.x=NULL
match_player12$id=NULL
match_player12$player_fifa_api_id.x=NULL
match_player12$player_fifa_api_id.y=NULL
#AP2
match_player13 <- merge(x = match_player12, y=player_atts,by.x='away_player_2',by.y='player_api_id',all.x=TRUE)
match_player13$date.x<-ymd(match_player13$date.x)
match_player13$date<-ymd_hms(match_player13$date)
match_player13$time_diff <- difftime(match_player13$date.x, match_player13$date,units='days')
match_player13 = match_player13[match_player13$time_diff >= 0,]
match_player13 = match_player13 %>%
  group_by(match_api_id, away_player_2) %>%
  filter(time_diff == min(time_diff))
for (i in 517:554){
  colnames(match_player13)[i] = paste(colnames(match_player13)[i], "aw_p_2", sep = "_")
}
for (i in 517:554){
  match_player13[[i]] = paste(match_player13[[i]],match_player13[[47]],sep="_")
}
match_player13$time_diff=NULL
match_player13$id.y = NULL
match_player13$date.y=NULL
match_player13$date=NULL
match_player13$id.x=NULL
match_player13$id=NULL
match_player13$player_fifa_api_id.x=NULL
match_player13$player_fifa_api_id.y=NULL

#AP3
match_player14 <- merge(x = match_player13, y=player_atts,by.x='away_player_3',by.y='player_api_id',all.x=TRUE)
match_player14$date.x<-ymd(match_player14$date.x)
match_player14$date<-ymd_hms(match_player14$date)
match_player14$time_diff <- difftime(match_player14$date.x, match_player14$date,units='days')
match_player14 = match_player14[match_player14$time_diff >= 0,]
match_player14 = match_player14 %>%
  group_by(match_api_id, away_player_3) %>%
  filter(time_diff == min(time_diff))
for (i in 554:591){
  colnames(match_player14)[i] = paste(colnames(match_player14)[i], "aw_p_3", sep = "_")
}
for (i in 554:591){
  match_player14[[i]] = paste(match_player14[[i]],match_player14[[48]],sep="_")
}
match_player14$time_diff=NULL
match_player14$id.y = NULL
match_player14$date.y=NULL
match_player14$date=NULL
match_player14$id.x=NULL
match_player14$id=NULL
match_player14$player_fifa_api_id.x=NULL
match_player14$player_fifa_api_id.y=NULL

#AP4
match_player15 <- merge(x = match_player14, y=player_atts,by.x='away_player_4',by.y='player_api_id',all.x=TRUE)
match_player15$date.x<-ymd(match_player15$date.x)
match_player15$date<-ymd_hms(match_player15$date)
match_player15$time_diff <- difftime(match_player15$date.x, match_player15$date,units='days')
match_player15 = match_player15[match_player15$time_diff >= 0,]
match_player15 = match_player15 %>%
  group_by(match_api_id, away_player_4) %>%
  filter(time_diff == min(time_diff))
for (i in 593:630){
  colnames(match_player15)[i] = paste(colnames(match_player15)[i], "aw_p_4", sep = "_")
}
for (i in 593:630){
  match_player15[[i]] = paste(match_player15[[i]],match_player15[[49]],sep="_")
}
match_player15$time_diff=NULL
match_player15$id.y = NULL
match_player15$date.y=NULL
match_player15$date=NULL
match_player15$id.x=NULL
match_player15$id=NULL
match_player15$player_fifa_api_id.x=NULL
match_player15$player_fifa_api_id.y=NULL

#AP5
match_player16 <- merge(x = match_player15, y=player_atts,by.x='away_player_5',by.y='player_api_id',all.x=TRUE)
match_player16$date.x<-ymd(match_player16$date.x)
match_player16$date<-ymd_hms(match_player16$date)
match_player16$time_diff <- difftime(match_player16$date.x, match_player16$date,units='days')
match_player16 = match_player16[match_player16$time_diff >= 0,]
match_player16 = match_player16 %>%
  group_by(match_api_id, away_player_5) %>%
  filter(time_diff == min(time_diff))
for (i in 630:667){
  colnames(match_player16)[i] = paste(colnames(match_player16)[i], "aw_p_5", sep = "_")
}
for (i in 630:667){
  match_player16[[i]] = paste(match_player16[[i]],match_player16[[50]],sep="_")
}
match_player16$time_diff=NULL
match_player16$id.y = NULL
match_player16$date.y=NULL
match_player16$date=NULL
match_player16$id.x=NULL
match_player16$id=NULL
match_player16$player_fifa_api_id.x=NULL
match_player16$player_fifa_api_id.y=NULL
#AP6
match_player17 <- merge(x = match_player16, y=player_atts,by.x='away_player_6',by.y='player_api_id',all.x=TRUE)
match_player17$date.x<-ymd(match_player17$date.x)
match_player17$date<-ymd_hms(match_player17$date)
match_player17$time_diff <- difftime(match_player17$date.x, match_player17$date,units='days')
match_player17 = match_player17[match_player17$time_diff >= 0,]
match_player17 = match_player17 %>%
  group_by(match_api_id, away_player_6) %>%
  filter(time_diff == min(time_diff))
for (i in 669:706){
  colnames(match_player17)[i] = paste(colnames(match_player17)[i], "aw_p_6", sep = "_")
}
for (i in 669:706){
  match_player17[[i]] = paste(match_player17[[i]],match_player17[[51]],sep="_")
}
match_player17$time_diff=NULL
match_player17$id.y = NULL
match_player17$date.y=NULL
match_player17$date=NULL
match_player17$id.x=NULL
match_player17$id=NULL
match_player17$player_fifa_api_id.x=NULL
match_player17$player_fifa_api_id.y=NULL
#AP7
match_player18 <- merge(x = match_player17, y=player_atts,by.x='away_player_7',by.y='player_api_id',all.x=TRUE)
match_player18$date.x<-ymd(match_player18$date.x)
match_player18$date<-ymd_hms(match_player18$date)
match_player18$time_diff <- difftime(match_player18$date.x, match_player18$date,units='days')
match_player18 = match_player18[match_player18$time_diff >= 0,]
match_player18 = match_player18 %>%
  group_by(match_api_id, away_player_7) %>%
  filter(time_diff == min(time_diff))
for (i in 706:743){
  colnames(match_player18)[i] = paste(colnames(match_player18)[i], "aw_p_7", sep = "_")
}
for (i in 706:743){
  match_player18[[i]] = paste(match_player18[[i]],match_player18[[52]],sep="_")
}
match_player18$time_diff=NULL
match_player18$id.y = NULL
match_player18$date.y=NULL
match_player18$date=NULL
match_player18$id.x=NULL
match_player18$id=NULL
match_player18$player_fifa_api_id.x=NULL
match_player18$player_fifa_api_id.y=NULL
#AP8
match_player19 <- merge(x = match_player18, y=player_atts,by.x='away_player_8',by.y='player_api_id',all.x=TRUE)
match_player19$date.x<-ymd(match_player19$date.x)
match_player19$date<-ymd_hms(match_player19$date)
match_player19$time_diff <- difftime(match_player19$date.x, match_player19$date,units='days')
match_player19 = match_player19[match_player19$time_diff >= 0,]
match_player19 = match_player19 %>%
  group_by(match_api_id, away_player_8) %>%
  filter(time_diff == min(time_diff))
for (i in 745:782){
  colnames(match_player19)[i] = paste(colnames(match_player19)[i], "aw_p_8", sep = "_")
}
for (i in 745:782){
  match_player19[[i]] = paste(match_player19[[i]],match_player19[[53]],sep="_")
}
match_player19$time_diff=NULL
match_player19$id.y = NULL
match_player19$date.y=NULL
match_player19$date=NULL
match_player19$id.x=NULL
match_player19$id=NULL
match_player19$player_fifa_api_id.x=NULL
match_player19$player_fifa_api_id.y=NULL
#AP9
match_player20 <- merge(x = match_player19, y=player_atts,by.x='away_player_9',by.y='player_api_id',all.x=TRUE)
match_player20$date.x<-ymd(match_player20$date.x)
match_player20$date<-ymd_hms(match_player20$date)
match_player20$time_diff <- difftime(match_player20$date.x, match_player20$date,units='days')
match_player20 = match_player20[match_player20$time_diff >= 0,]
match_player20 = match_player20 %>%
  group_by(match_api_id, away_player_9) %>%
  filter(time_diff == min(time_diff))
for (i in 782:819){
  colnames(match_player20)[i] = paste(colnames(match_player20)[i], "aw_p_9", sep = "_")
}
for (i in 782:819){
  match_player20[[i]] = paste(match_player20[[i]],match_player20[[54]],sep="_")
}
match_player20$time_diff=NULL
match_player20$id.y = NULL
match_player20$date.y=NULL
match_player20$date=NULL
match_player20$id.x=NULL
match_player20$id=NULL
match_player20$player_fifa_api_id.x=NULL
match_player20$player_fifa_api_id.y=NULL
#AP10
match_player21 <- merge(x = match_player20, y=player_atts,by.x='away_player_10',by.y='player_api_id',all.x=TRUE)
match_player21$date.x<-ymd(match_player21$date.x)
match_player21$date<-ymd_hms(match_player21$date)
match_player21$time_diff <- difftime(match_player21$date.x, match_player21$date,units='days')
match_player21 = match_player21[match_player21$time_diff >= 0,]
match_player21 = match_player21 %>%
  group_by(match_api_id, away_player_10) %>%
  filter(time_diff == min(time_diff))
for (i in 821:858){
  colnames(match_player21)[i] = paste(colnames(match_player21)[i], "aw_p_10", sep = "_")
}
for (i in 821:858){
  match_player21[[i]] = paste(match_player21[[i]],match_player21[[55]],sep="_")
}
match_player21$time_diff=NULL
match_player21$id.y = NULL
match_player21$date.y=NULL
match_player21$date=NULL
match_player21$id.x=NULL
match_player21$id=NULL
match_player21$player_fifa_api_id.x=NULL
match_player21$player_fifa_api_id.y=NULL
#AP11
match_player22 <- merge(x = match_player21, y=player_atts,by.x='away_player_11',by.y='player_api_id',all.x=TRUE)
match_player22$date.x<-ymd(match_player22$date.x)
match_player22$date<-ymd_hms(match_player22$date)
match_player22$time_diff <- difftime(match_player22$date.x, match_player22$date,units='days')
match_player22 = match_player22[match_player22$time_diff >= 0,]
match_player22 = match_player22 %>%
  group_by(match_api_id, away_player_11) %>%
  filter(time_diff == min(time_diff))
for (i in 858:895){
  colnames(match_player22)[i] = paste(colnames(match_player22)[i], "aw_p_11", sep = "_")
}
for (i in 858:895){
  match_player22[[i]] = paste(match_player22[[i]],match_player22[[56]],sep="_")
}
match_player22$time_diff=NULL
match_player22$id.y = NULL
match_player22$date.y=NULL
match_player22$date=NULL
match_player22$id.x=NULL
match_player22$id=NULL
match_player22$player_fifa_api_id.x=NULL
match_player22$player_fifa_api_id.y=NULL

################# ARules ##################
# all the matches that lose
loss_match = match_player22
### lose as home play, need to use away player attributes in the next steps
home_loss_match = loss_match[loss_match$opponent == loss_match$away_team_api_id,]
home_loss_ar = home_loss_match %>%
  select(preferred_foot_aw_p_1:gk_reflexes_Bucket_aw_p_11, result)
home_loss_ar = home_loss_ar[,-c(1,2)]
home_loss_ar = subset(home_loss_ar, select = -player_fifa_api_id)
### lose as away play, need to use home player attributes in the next steps
away_loss_match = loss_match[loss_match$opponent == loss_match$home_team_api_id,]
away_loss_ar = away_loss_match %>%
  select(preferred_foot_hp_1:gk_reflexes_Bucket_hp_11, result)
away_loss_ar = away_loss_ar[,-c(1,2)]
colnames(away_loss_ar) = colnames(home_loss_ar)
all_loss_ar = rbind(home_loss_ar, away_loss_ar)
##### add column name to values
column_names = names(all_loss_ar)

for (column in column_names) {
  all_loss_ar[[column]] = paste(column, all_loss_ar[[column]], sep = '_')
}

###### delete player numbers
for (i in 1:418) {
  for (j in 1:287) {
    all_loss_ar[j,i] = gsub('_aw_p_[0-9]', '', all_loss_ar[j,i])
  }
}
for (i in 1:418) {
  for (j in 1:287) {
    all_loss_ar[j,i] = gsub('[0-9]', '', all_loss_ar[j,i])
  }
}


write.csv(all_loss_ar,'palermo.csv')
```

  When we run the associations of player attributes that correspond to Palermo's loss, we found the following rules:
  
```{r, include = FALSE, message=FALSE, results="hide"}
palermo_all3 = read.transactions("palermo.csv", format = "basket",
                           sep = ",", rm.duplicates = TRUE, skip =1 , header = FALSE)

# inspect(palermo_all3)
# itemInfo(palermo_all3)
rules <- apriori(palermo_all3, parameter = list(supp = 0.2, conf = 0.3), appearance = list(rhs = 'result_loss'))

rules_lift = sort(rules,by='lift',decreasing = TRUE)

```
```{r, fig.width=16}
inspect(rules_lift[1:10])
```

```{r}
# plot(rules_lift[1:5], method = 'graph', engine = 'htmlwidget')
plot(rules_lift[1:10], method = 'paracoord')
```

##### Recommendations against Palermo

Midfield is the key to beating Palermo. Mid-fielders with high ball playing skills increase the chances of winning against Palermo. In addition, on occasions, high conversion accuracy from free kicks helps

If we can combine the above mid-field with defenders to mark the Palermo strikers, we push up our chances of win further up.


#### Genoa 

```{r, include = FALSE}
player_atts = player_atts_tbl %>% 
  collect()
long_team_name <- 'Genoa'
roma_record <- team_tbl %>% 
  collect() %>%
  filter(grepl(long_team_name, team_long_name))
home_matches <- match %>%
  filter(home_team_api_id == roma_record$team_api_id) %>%
  mutate(goal_diff = home_team_goal - away_team_goal) %>%
  mutate(type = 'home', opponent = away_team_api_id)
# hist(home_matches$goal_diff)
# summary(home_matches$goal_diff)

away_matches <- match %>%
  filter(away_team_api_id == roma_record$team_api_id) %>%
  mutate(goal_diff =away_team_goal - home_team_goal) %>%
  mutate(type = 'away', opponent = home_team_api_id)

# hist(away_matches$goal_diff)
# summary(away_matches$goal_diff)

all_match = rbind(home_matches, away_matches)
# ggplot(all_match, aes(type, goal_diff, col = type)) +
#   geom_boxplot()

all_match$result = as.numeric(all_match$goal_diff)
all_match[all_match$goal_diff > 0, ]$result = 'win'
all_match[all_match$goal_diff < 0, ]$result = 'loss'
all_match[all_match$goal_diff == 0, ]$result = 'draw'
# ggplot(all_match, aes(result)) +
#   geom_bar()

# ggplot(all_match[all_match$result == 'lose',], aes(as.factor(opponent))) +
#   geom_bar()

##################### position ###################
for (i in 1:11){
  x = paste("home_player_X",i,sep='')
  y = paste("home_player_Y",i,sep='')
  inp = paste("hm_ply_pos",i,sep="_")
  all_match[inp] = ifelse(all_match[x]==1 & all_match[y]==1,"Goaly",
                      ifelse(all_match[y]>=2 & all_match[y]<=5,"Defender",
                             ifelse(all_match[y]>=6 & all_match[y]<=8,"Mid Fielders",
                                    ifelse(all_match[y]>=9 & all_match[y]<=11,"Forwards","NA"))))
}

for (i in 1:11){
  x = paste("away_player_X",i,sep='')
  y = paste("away_player_Y",i,sep='')
  inp = paste("away_ply_pos",i,sep="_")
  all_match[inp] = ifelse(all_match[x]==1 & all_match[y]==1,"Goaly",
                      ifelse(all_match[y]>=2 & all_match[y]<=5,"Defender",
                             ifelse(all_match[y]>=6 & all_match[y]<=8,"Mid Fielders",
                                    ifelse(all_match[y]>=9 & all_match[y]<=11,"Forwards","NA"))))
}
```

```{r, include = FALSE}
column_names = c("overall_rating","potential","crossing", "finishing","heading_accuracy",    
                 "short_passing", "volleys","dribbling",    
                 "curve", "free_kick_accuracy" ,"long_passing",    
                 "ball_control","acceleration","sprint_speed",    
                 "agility","reactions","balance",    
                 "shot_power","jumping","stamina",    
                 "strength","long_shots","aggression",    
                 "interceptions","positioning","vision",    
                 "penalties", "marking","standing_tackle",
                 "sliding_tackle","gk_diving","gk_handling",    
                 "gk_kicking","gk_positioning","gk_reflexes")

for (i in column_names){
  k = paste(i, "Bucket",sep="_")
  player_atts[k] = 
    cut(player_atts[[i]], breaks = 5, labels=c('low','low-med','med','med-high','high'))
}

player_atts <- select(player_atts, c(1:9, overall_rating_Bucket:gk_reflexes_Bucket))
player_atts = player_atts[, -c(5,6)]
all_match <- select(all_match, c(id:away_team_goal, home_player_1:away_player_11, opponent:away_ply_pos_11))

#######
# match_g <- gather(all_match, player, player_id, home_player_1:away_player_11, na.rm = TRUE)
# View(match_g)
# match_s <- arrange(match_g, match_api_id, player)
# View(match_s)
# #match_s <- select(match_s, c(1:10, player, player_id))
# colnames(match_s)[37] <- "player_api_id"

#HP1
match_player <- merge(x = all_match, y=player_atts,by.x='home_player_1',by.y='player_api_id',all.x=TRUE)
match_player$date.x<-ymd_hms(match_player$date.x)
match_player$date.y<-ymd_hms(match_player$date.y)
match_player$time_diff <- difftime(match_player$date.x, match_player$date.y,units='days')
match_player = match_player[match_player$time_diff >= 0,]
match_player_1 = match_player %>%
  group_by(match_api_id, home_player_1) %>%
  filter(time_diff == min(time_diff))
for (i in 61:98){
  colnames(match_player_1)[i] = paste(colnames(match_player_1)[i], "hp_1", sep = "_")
  }
for (i in 61:98){
  match_player_1[[i]] = paste(match_player_1[[i]],match_player_1[[36]],sep="_")
}
match_player_1$time_diff=NULL
# HP2

match_player2 <- merge(x = match_player_1, y=player_atts,by.x='home_player_2',by.y='player_api_id',all.x=TRUE)
match_player2$date.x<-ymd(match_player2$date.x)
match_player2$date<-ymd_hms(match_player2$date)
match_player2$time_diff <- difftime(match_player2$date.x, match_player2$date,units='days')
match_player2 = match_player2[match_player2$time_diff >= 0,]
match_player2 = match_player2 %>%
  group_by(match_api_id, home_player_2) %>%
  filter(time_diff == min(time_diff))
for (i in 102:139){
  colnames(match_player2)[i] = paste(colnames(match_player2)[i], "hp_2", sep = "_")
}
for (i in 102:139){
  match_player2[[i]] = paste(match_player2[[i]],match_player2[[37]],sep="_")
}
match_player2$time_diff=NULL
match_player2$id.y = NULL
match_player2$date.y=NULL
match_player2$date=NULL
match_player2$id.x=NULL
##
#HP3

match_player3 <- merge(x = match_player2, y=player_atts,by.x='home_player_3',by.y='player_api_id',all.x=TRUE)
match_player3$date.x<-ymd(match_player3$date.x)
match_player3$date<-ymd_hms(match_player3$date)
match_player3$time_diff <- difftime(match_player3$date.x, match_player3$date,units='days')
match_player3 = match_player3[match_player3$time_diff >= 0,]
match_player3 = match_player3 %>%
  group_by(match_api_id, home_player_3) %>%
  filter(time_diff == min(time_diff))
for (i in 139:176){
  colnames(match_player3)[i] = paste(colnames(match_player3)[i], "hp_3", sep = "_")
}
for (i in 139:176){
  match_player3[[i]] = paste(match_player3[[i]],match_player3[[37]],sep="_")
}
match_player3$time_diff=NULL
match_player3$id.y = NULL
match_player3$date.y=NULL
match_player3$date=NULL
match_player3$id.x=NULL
match_player3$player_fifa_api_id=NULL

#HP4

match_player4 <- merge(x = match_player3, y=player_atts,by.x='home_player_4',by.y='player_api_id',all.x=TRUE)
match_player4$date.x<-ymd(match_player4$date.x)
match_player4$date<-ymd_hms(match_player4$date)
match_player4$time_diff <- difftime(match_player4$date.x, match_player4$date,units='days')
match_player4 = match_player4[match_player4$time_diff >= 0,]
match_player4 = match_player4 %>%
  group_by(match_api_id, home_player_4) %>%
  filter(time_diff == min(time_diff))
for (i in 176:213){
  colnames(match_player4)[i] = paste(colnames(match_player4)[i], "hp_4", sep = "_")
}
for (i in 176:213){
  match_player4[[i]] = paste(match_player4[[i]],match_player4[[38]],sep="_")
}
match_player4$time_diff=NULL
match_player4$id.y = NULL
match_player4$date.y=NULL
match_player4$date=NULL
match_player4$id.x=NULL
match_player4$id=NULL
match_player4$player_fifa_api_id.x=NULL
match_player4$player_fifa_api_id.y=NULL
#HP5

match_player5 <- merge(x = match_player4, y=player_atts,by.x='home_player_5',by.y='player_api_id',all.x=TRUE)
match_player5$date.x<-ymd(match_player5$date.x)
match_player5$date<-ymd_hms(match_player5$date)
match_player5$time_diff <- difftime(match_player5$date.x, match_player5$date,units='days')
match_player5 = match_player5[match_player5$time_diff >= 0,]
match_player5 = match_player5 %>%
  group_by(match_api_id, home_player_5) %>%
  filter(time_diff == min(time_diff))
for (i in 213:250){
  colnames(match_player5)[i] = paste(colnames(match_player5)[i], "hp_5", sep = "_")
}
for (i in 213:250){
  match_player5[[i]] = paste(match_player5[[i]],match_player5[[39]],sep="_")
}
match_player5$time_diff=NULL
match_player5$id.y = NULL
match_player5$date.y=NULL
match_player5$date=NULL
match_player5$id.x=NULL
match_player5$id=NULL
###
#HP6
match_player6 <- merge(x = match_player5, y=player_atts,by.x='home_player_6',by.y='player_api_id',all.x=TRUE)
match_player6$date.x<-ymd(match_player6$date.x)
match_player6$date<-ymd_hms(match_player6$date)
match_player6$time_diff <- difftime(match_player6$date.x, match_player6$date,units='days')
match_player6 = match_player6[match_player6$time_diff >= 0,]
match_player6 = match_player6 %>%
  group_by(match_api_id, home_player_6) %>%
  filter(time_diff == min(time_diff))
for (i in 252:289){
  colnames(match_player6)[i] = paste(colnames(match_player6)[i], "hp_6", sep = "_")
}
for (i in 252:289){
  match_player6[[i]] = paste(match_player6[[i]],match_player6[[40]],sep="_")
}
match_player6$time_diff=NULL
match_player6$id.y = NULL
match_player6$date.y=NULL
match_player6$date=NULL
match_player6$id.x=NULL
match_player6$id=NULL
match_player6$player_fifa_api_id.x=NULL
match_player6$player_fifa_api_id.y=NULL

#HP7
match_player7 <- merge(x = match_player6, y=player_atts,by.x='home_player_7',by.y='player_api_id',all.x=TRUE)
match_player7$date.x<-ymd(match_player7$date.x)
match_player7$date<-ymd_hms(match_player7$date)
match_player7$time_diff <- difftime(match_player7$date.x, match_player7$date,units='days')
match_player7 = match_player7[match_player7$time_diff >= 0,]
match_player7 = match_player7 %>%
  group_by(match_api_id, home_player_7) %>%
  filter(time_diff == min(time_diff))
for (i in 289:326){
  colnames(match_player7)[i] = paste(colnames(match_player7)[i], "hp_7", sep = "_")
}
for (i in 289:326){
  match_player7[[i]] = paste(match_player7[[i]],match_player7[[41]],sep="_")
}
match_player7$time_diff=NULL
match_player7$id.y = NULL
match_player7$date.y=NULL
match_player7$date=NULL
match_player7$id.x=NULL
match_player7$id=NULL
match_player7$player_fifa_api_id.x=NULL
match_player7$player_fifa_api_id.y=NULL

#HP8
match_player8 <- merge(x = match_player7, y=player_atts,by.x='home_player_8',by.y='player_api_id',all.x=TRUE)
match_player8$date.x<-ymd(match_player8$date.x)
match_player8$date<-ymd_hms(match_player8$date)
match_player8$time_diff <- difftime(match_player8$date.x, match_player8$date,units='days')
match_player8 = match_player8[match_player8$time_diff >= 0,]
match_player8 = match_player8 %>%
  group_by(match_api_id, home_player_8) %>%
  filter(time_diff == min(time_diff))
for (i in 326:363){
  colnames(match_player8)[i] = paste(colnames(match_player8)[i], "hp_8", sep = "_")
}
for (i in 326:363){
  match_player8[[i]] = paste(match_player8[[i]],match_player8[[42]],sep="_")
}
match_player8$time_diff=NULL
match_player8$id.y = NULL
match_player8$date.y=NULL
match_player8$date=NULL
match_player8$id.x=NULL
match_player8$id=NULL
match_player8$player_fifa_api_id.x=NULL
match_player8$player_fifa_api_id.y=NULL

#HP9
match_player9 <- merge(x = match_player8, y=player_atts,by.x='home_player_9',by.y='player_api_id',all.x=TRUE)
match_player9$date.x<-ymd(match_player9$date.x)
match_player9$date<-ymd_hms(match_player9$date)
match_player9$time_diff <- difftime(match_player9$date.x, match_player9$date,units='days')
match_player9 = match_player9[match_player9$time_diff >= 0,]
match_player9 = match_player9 %>%
  group_by(match_api_id, home_player_9) %>%
  filter(time_diff == min(time_diff))
for (i in 365:402){
  colnames(match_player9)[i] = paste(colnames(match_player9)[i], "hp_9", sep = "_")
}
for (i in 365:402){
  match_player9[[i]] = paste(match_player9[[i]],match_player9[[43]],sep="_")
}
match_player9$time_diff=NULL
match_player9$id.y = NULL
match_player9$date.y=NULL
match_player9$date=NULL
match_player9$id.x=NULL
match_player9$id=NULL
match_player9$player_fifa_api_id.x=NULL
match_player9$player_fifa_api_id.y=NULL

#HP10
match_player10 <- merge(x = match_player9, y=player_atts,by.x='home_player_10',by.y='player_api_id',all.x=TRUE)
match_player10$date.x<-ymd(match_player10$date.x)
match_player10$date<-ymd_hms(match_player10$date)
match_player10$time_diff <- difftime(match_player10$date.x, match_player10$date,units='days')
match_player10 = match_player10[match_player10$time_diff >= 0,]
match_player10 = match_player10 %>%
  group_by(match_api_id, home_player_10) %>%
  filter(time_diff == min(time_diff))
for (i in 402:439){
  colnames(match_player10)[i] = paste(colnames(match_player10)[i], "hp_10", sep = "_")
}
for (i in 402:439){
  match_player10[[i]] = paste(match_player10[[i]],match_player10[[44]],sep="_")
}
match_player10$time_diff=NULL
match_player10$id.y = NULL
match_player10$date.y=NULL
match_player10$date=NULL
match_player10$id.x=NULL
match_player10$id=NULL
match_player10$player_fifa_api_id.x=NULL
match_player10$player_fifa_api_id.y=NULL

#HP11
match_player11 <- merge(x = match_player10, y=player_atts,by.x='home_player_11',by.y='player_api_id',all.x=TRUE)
match_player11$date.x<-ymd(match_player11$date.x)
match_player11$date<-ymd_hms(match_player11$date)
match_player11$time_diff <- difftime(match_player11$date.x, match_player11$date,units='days')
match_player11 = match_player11[match_player11$time_diff >= 0,]
match_player11 = match_player11 %>%
  group_by(match_api_id, home_player_11) %>%
  filter(time_diff == min(time_diff))
for (i in 441:478){
  colnames(match_player11)[i] = paste(colnames(match_player11)[i], "hp_11", sep = "_")
}
for (i in 441:478){
  match_player11[[i]] = paste(match_player11[[i]],match_player11[[45]],sep="_")
}
match_player11$time_diff=NULL
match_player11$id.y = NULL
match_player11$date.y=NULL
match_player11$date=NULL
match_player11$id.x=NULL
match_player11$id=NULL
match_player11$player_fifa_api_id.x=NULL
match_player11$player_fifa_api_id.y=NULL

#AP1

match_player12 <- merge(x = match_player11, y=player_atts,by.x='away_player_1',by.y='player_api_id',all.x=TRUE)
match_player12$date.x<-ymd(match_player12$date.x)
match_player12$date<-ymd_hms(match_player12$date)
match_player12$time_diff <- difftime(match_player12$date.x, match_player12$date,units='days')
match_player12 = match_player12[match_player12$time_diff >= 0,]
match_player12 = match_player12 %>%
  group_by(match_api_id, away_player_1) %>%
  filter(time_diff == min(time_diff))
for (i in 478:515){
  colnames(match_player12)[i] = paste(colnames(match_player12)[i], "aw_p_1", sep = "_")
}
for (i in 478:515){
  match_player12[[i]] = paste(match_player12[[i]],match_player12[[46]],sep="_")
}
match_player12$time_diff=NULL
match_player12$id.y = NULL
match_player12$date.y=NULL
match_player12$date=NULL
match_player12$id.x=NULL
match_player12$id=NULL
match_player12$player_fifa_api_id.x=NULL
match_player12$player_fifa_api_id.y=NULL
#AP2
match_player13 <- merge(x = match_player12, y=player_atts,by.x='away_player_2',by.y='player_api_id',all.x=TRUE)
match_player13$date.x<-ymd(match_player13$date.x)
match_player13$date<-ymd_hms(match_player13$date)
match_player13$time_diff <- difftime(match_player13$date.x, match_player13$date,units='days')
match_player13 = match_player13[match_player13$time_diff >= 0,]
match_player13 = match_player13 %>%
  group_by(match_api_id, away_player_2) %>%
  filter(time_diff == min(time_diff))
for (i in 517:554){
  colnames(match_player13)[i] = paste(colnames(match_player13)[i], "aw_p_2", sep = "_")
}
for (i in 517:554){
  match_player13[[i]] = paste(match_player13[[i]],match_player13[[47]],sep="_")
}
match_player13$time_diff=NULL
match_player13$id.y = NULL
match_player13$date.y=NULL
match_player13$date=NULL
match_player13$id.x=NULL
match_player13$id=NULL
match_player13$player_fifa_api_id.x=NULL
match_player13$player_fifa_api_id.y=NULL

#AP3
match_player14 <- merge(x = match_player13, y=player_atts,by.x='away_player_3',by.y='player_api_id',all.x=TRUE)
match_player14$date.x<-ymd(match_player14$date.x)
match_player14$date<-ymd_hms(match_player14$date)
match_player14$time_diff <- difftime(match_player14$date.x, match_player14$date,units='days')
match_player14 = match_player14[match_player14$time_diff >= 0,]
match_player14 = match_player14 %>%
  group_by(match_api_id, away_player_3) %>%
  filter(time_diff == min(time_diff))
for (i in 554:591){
  colnames(match_player14)[i] = paste(colnames(match_player14)[i], "aw_p_3", sep = "_")
}
for (i in 554:591){
  match_player14[[i]] = paste(match_player14[[i]],match_player14[[48]],sep="_")
}
match_player14$time_diff=NULL
match_player14$id.y = NULL
match_player14$date.y=NULL
match_player14$date=NULL
match_player14$id.x=NULL
match_player14$id=NULL
match_player14$player_fifa_api_id.x=NULL
match_player14$player_fifa_api_id.y=NULL

#AP4
match_player15 <- merge(x = match_player14, y=player_atts,by.x='away_player_4',by.y='player_api_id',all.x=TRUE)
match_player15$date.x<-ymd(match_player15$date.x)
match_player15$date<-ymd_hms(match_player15$date)
match_player15$time_diff <- difftime(match_player15$date.x, match_player15$date,units='days')
match_player15 = match_player15[match_player15$time_diff >= 0,]
match_player15 = match_player15 %>%
  group_by(match_api_id, away_player_4) %>%
  filter(time_diff == min(time_diff))
for (i in 593:630){
  colnames(match_player15)[i] = paste(colnames(match_player15)[i], "aw_p_4", sep = "_")
}
for (i in 593:630){
  match_player15[[i]] = paste(match_player15[[i]],match_player15[[49]],sep="_")
}
match_player15$time_diff=NULL
match_player15$id.y = NULL
match_player15$date.y=NULL
match_player15$date=NULL
match_player15$id.x=NULL
match_player15$id=NULL
match_player15$player_fifa_api_id.x=NULL
match_player15$player_fifa_api_id.y=NULL

#AP5
match_player16 <- merge(x = match_player15, y=player_atts,by.x='away_player_5',by.y='player_api_id',all.x=TRUE)
match_player16$date.x<-ymd(match_player16$date.x)
match_player16$date<-ymd_hms(match_player16$date)
match_player16$time_diff <- difftime(match_player16$date.x, match_player16$date,units='days')
match_player16 = match_player16[match_player16$time_diff >= 0,]
match_player16 = match_player16 %>%
  group_by(match_api_id, away_player_5) %>%
  filter(time_diff == min(time_diff))
for (i in 630:667){
  colnames(match_player16)[i] = paste(colnames(match_player16)[i], "aw_p_5", sep = "_")
}
for (i in 630:667){
  match_player16[[i]] = paste(match_player16[[i]],match_player16[[50]],sep="_")
}
match_player16$time_diff=NULL
match_player16$id.y = NULL
match_player16$date.y=NULL
match_player16$date=NULL
match_player16$id.x=NULL
match_player16$id=NULL
match_player16$player_fifa_api_id.x=NULL
match_player16$player_fifa_api_id.y=NULL
#AP6
match_player17 <- merge(x = match_player16, y=player_atts,by.x='away_player_6',by.y='player_api_id',all.x=TRUE)
match_player17$date.x<-ymd(match_player17$date.x)
match_player17$date<-ymd_hms(match_player17$date)
match_player17$time_diff <- difftime(match_player17$date.x, match_player17$date,units='days')
match_player17 = match_player17[match_player17$time_diff >= 0,]
match_player17 = match_player17 %>%
  group_by(match_api_id, away_player_6) %>%
  filter(time_diff == min(time_diff))
for (i in 669:706){
  colnames(match_player17)[i] = paste(colnames(match_player17)[i], "aw_p_6", sep = "_")
}
for (i in 669:706){
  match_player17[[i]] = paste(match_player17[[i]],match_player17[[51]],sep="_")
}
match_player17$time_diff=NULL
match_player17$id.y = NULL
match_player17$date.y=NULL
match_player17$date=NULL
match_player17$id.x=NULL
match_player17$id=NULL
match_player17$player_fifa_api_id.x=NULL
match_player17$player_fifa_api_id.y=NULL
#AP7
match_player18 <- merge(x = match_player17, y=player_atts,by.x='away_player_7',by.y='player_api_id',all.x=TRUE)
match_player18$date.x<-ymd(match_player18$date.x)
match_player18$date<-ymd_hms(match_player18$date)
match_player18$time_diff <- difftime(match_player18$date.x, match_player18$date,units='days')
match_player18 = match_player18[match_player18$time_diff >= 0,]
match_player18 = match_player18 %>%
  group_by(match_api_id, away_player_7) %>%
  filter(time_diff == min(time_diff))
for (i in 706:743){
  colnames(match_player18)[i] = paste(colnames(match_player18)[i], "aw_p_7", sep = "_")
}
for (i in 706:743){
  match_player18[[i]] = paste(match_player18[[i]],match_player18[[52]],sep="_")
}
match_player18$time_diff=NULL
match_player18$id.y = NULL
match_player18$date.y=NULL
match_player18$date=NULL
match_player18$id.x=NULL
match_player18$id=NULL
match_player18$player_fifa_api_id.x=NULL
match_player18$player_fifa_api_id.y=NULL
#AP8
match_player19 <- merge(x = match_player18, y=player_atts,by.x='away_player_8',by.y='player_api_id',all.x=TRUE)
match_player19$date.x<-ymd(match_player19$date.x)
match_player19$date<-ymd_hms(match_player19$date)
match_player19$time_diff <- difftime(match_player19$date.x, match_player19$date,units='days')
match_player19 = match_player19[match_player19$time_diff >= 0,]
match_player19 = match_player19 %>%
  group_by(match_api_id, away_player_8) %>%
  filter(time_diff == min(time_diff))
for (i in 745:782){
  colnames(match_player19)[i] = paste(colnames(match_player19)[i], "aw_p_8", sep = "_")
}
for (i in 745:782){
  match_player19[[i]] = paste(match_player19[[i]],match_player19[[53]],sep="_")
}
match_player19$time_diff=NULL
match_player19$id.y = NULL
match_player19$date.y=NULL
match_player19$date=NULL
match_player19$id.x=NULL
match_player19$id=NULL
match_player19$player_fifa_api_id.x=NULL
match_player19$player_fifa_api_id.y=NULL
#AP9
match_player20 <- merge(x = match_player19, y=player_atts,by.x='away_player_9',by.y='player_api_id',all.x=TRUE)
match_player20$date.x<-ymd(match_player20$date.x)
match_player20$date<-ymd_hms(match_player20$date)
match_player20$time_diff <- difftime(match_player20$date.x, match_player20$date,units='days')
match_player20 = match_player20[match_player20$time_diff >= 0,]
match_player20 = match_player20 %>%
  group_by(match_api_id, away_player_9) %>%
  filter(time_diff == min(time_diff))
for (i in 782:819){
  colnames(match_player20)[i] = paste(colnames(match_player20)[i], "aw_p_9", sep = "_")
}
for (i in 782:819){
  match_player20[[i]] = paste(match_player20[[i]],match_player20[[54]],sep="_")
}
match_player20$time_diff=NULL
match_player20$id.y = NULL
match_player20$date.y=NULL
match_player20$date=NULL
match_player20$id.x=NULL
match_player20$id=NULL
match_player20$player_fifa_api_id.x=NULL
match_player20$player_fifa_api_id.y=NULL
#AP10
match_player21 <- merge(x = match_player20, y=player_atts,by.x='away_player_10',by.y='player_api_id',all.x=TRUE)
match_player21$date.x<-ymd(match_player21$date.x)
match_player21$date<-ymd_hms(match_player21$date)
match_player21$time_diff <- difftime(match_player21$date.x, match_player21$date,units='days')
match_player21 = match_player21[match_player21$time_diff >= 0,]
match_player21 = match_player21 %>%
  group_by(match_api_id, away_player_10) %>%
  filter(time_diff == min(time_diff))
for (i in 821:858){
  colnames(match_player21)[i] = paste(colnames(match_player21)[i], "aw_p_10", sep = "_")
}
for (i in 821:858){
  match_player21[[i]] = paste(match_player21[[i]],match_player21[[55]],sep="_")
}
match_player21$time_diff=NULL
match_player21$id.y = NULL
match_player21$date.y=NULL
match_player21$date=NULL
match_player21$id.x=NULL
match_player21$id=NULL
match_player21$player_fifa_api_id.x=NULL
match_player21$player_fifa_api_id.y=NULL
#AP11
match_player22 <- merge(x = match_player21, y=player_atts,by.x='away_player_11',by.y='player_api_id',all.x=TRUE)
match_player22$date.x<-ymd(match_player22$date.x)
match_player22$date<-ymd_hms(match_player22$date)
match_player22$time_diff <- difftime(match_player22$date.x, match_player22$date,units='days')
match_player22 = match_player22[match_player22$time_diff >= 0,]
match_player22 = match_player22 %>%
  group_by(match_api_id, away_player_11) %>%
  filter(time_diff == min(time_diff))
for (i in 858:895){
  colnames(match_player22)[i] = paste(colnames(match_player22)[i], "aw_p_11", sep = "_")
}
for (i in 858:895){
  match_player22[[i]] = paste(match_player22[[i]],match_player22[[56]],sep="_")
}
match_player22$time_diff=NULL
match_player22$id.y = NULL
match_player22$date.y=NULL
match_player22$date=NULL
match_player22$id.x=NULL
match_player22$id=NULL
match_player22$player_fifa_api_id.x=NULL
match_player22$player_fifa_api_id.y=NULL

################# ARules ##################
# all the matches that lose
loss_match = match_player22
### lose as home play, need to use away player attributes in the next steps
home_loss_match = loss_match[loss_match$opponent == loss_match$away_team_api_id,]
home_loss_ar = home_loss_match %>%
  select(preferred_foot_aw_p_1:gk_reflexes_Bucket_aw_p_11, result)
home_loss_ar = home_loss_ar[,-c(1,2)]
home_loss_ar = subset(home_loss_ar, select = -player_fifa_api_id)
### lose as away play, need to use home player attributes in the next steps
away_loss_match = loss_match[loss_match$opponent == loss_match$home_team_api_id,]
away_loss_ar = away_loss_match %>%
  select(preferred_foot_hp_1:gk_reflexes_Bucket_hp_11, result)
away_loss_ar = away_loss_ar[,-c(1,2)]
colnames(away_loss_ar) = colnames(home_loss_ar)
all_loss_ar = rbind(home_loss_ar, away_loss_ar)
##### add column name to values
column_names = names(all_loss_ar)

for (column in column_names) {
  all_loss_ar[[column]] = paste(column, all_loss_ar[[column]], sep = '_')
}

###### delete player numbers
for (i in 1:418) {
  for (j in 1:287) {
    all_loss_ar[j,i] = gsub('_aw_p_[0-9]', '', all_loss_ar[j,i])
  }
}
for (i in 1:418) {
  for (j in 1:287) {
    all_loss_ar[j,i] = gsub('[0-9]', '', all_loss_ar[j,i])
  }
}


write.csv(all_loss_ar,'genoa.csv')
```

```{r include=FALSE, warning=FALSE, results="hide"}
genoa_all3 = read.transactions("genoa.csv", format = "basket",
                           sep = ",", rm.duplicates = TRUE, skip =1 , header = FALSE)
# inspect(genoa_all3)
# itemInfo(genoa_all3)
rules <- apriori(genoa_all3, parameter = list(supp = 0.2, conf = 0.3), appearance = list(rhs = 'result_loss'))

rules_lift = sort(rules,by='lift',decreasing = TRUE)

```
  
  When we run the associations of player attributes that correspond to Genoa's loss, we found the following rules:  
  
```{r, fig.width=16}
inspect(rules_lift[1:10])
```

```{r}
# plot(rules_lift[1:5], method = 'graph', engine = 'htmlwidget')
plot(rules_lift[1:10], method = 'paracoord')
```
  
##### Recommendations against Genoa

Against Genoa as well, mid-field is the key as a midfielder's scoring ability leads to more wins than often.


#### Napoli 

```{r, include = FALSE}
player_atts = player_atts_tbl %>% 
  collect()
long_team_name <- 'Napoli'
roma_record <- team_tbl %>% 
  collect() %>%
  filter(grepl(long_team_name, team_long_name))
home_matches <- match %>%
  filter(home_team_api_id == roma_record$team_api_id) %>%
  mutate(goal_diff = home_team_goal - away_team_goal) %>%
  mutate(type = 'home', opponent = away_team_api_id)
# hist(home_matches$goal_diff)
# summary(home_matches$goal_diff)

away_matches <- match %>%
  filter(away_team_api_id == roma_record$team_api_id) %>%
  mutate(goal_diff =away_team_goal - home_team_goal) %>%
  mutate(type = 'away', opponent = home_team_api_id)

# hist(away_matches$goal_diff)
# summary(away_matches$goal_diff)

all_match = rbind(home_matches, away_matches)
# ggplot(all_match, aes(type, goal_diff, col = type)) +
#   geom_boxplot()

all_match$result = as.numeric(all_match$goal_diff)
all_match[all_match$goal_diff > 0, ]$result = 'win'
all_match[all_match$goal_diff < 0, ]$result = 'loss'
all_match[all_match$goal_diff == 0, ]$result = 'draw'
# ggplot(all_match, aes(result)) +
#   geom_bar()

# ggplot(all_match[all_match$result == 'lose',], aes(as.factor(opponent))) +
#   geom_bar()

##################### position ###################
for (i in 1:11){
  x = paste("home_player_X",i,sep='')
  y = paste("home_player_Y",i,sep='')
  inp = paste("hm_ply_pos",i,sep="_")
  all_match[inp] = ifelse(all_match[x]==1 & all_match[y]==1,"Goaly",
                      ifelse(all_match[y]>=2 & all_match[y]<=5,"Defender",
                             ifelse(all_match[y]>=6 & all_match[y]<=8,"Mid Fielders",
                                    ifelse(all_match[y]>=9 & all_match[y]<=11,"Forwards","NA"))))
}

for (i in 1:11){
  x = paste("away_player_X",i,sep='')
  y = paste("away_player_Y",i,sep='')
  inp = paste("away_ply_pos",i,sep="_")
  all_match[inp] = ifelse(all_match[x]==1 & all_match[y]==1,"Goaly",
                      ifelse(all_match[y]>=2 & all_match[y]<=5,"Defender",
                             ifelse(all_match[y]>=6 & all_match[y]<=8,"Mid Fielders",
                                    ifelse(all_match[y]>=9 & all_match[y]<=11,"Forwards","NA"))))
}
```

```{r,include=FALSE}
column_names = c("overall_rating","potential","crossing", "finishing","heading_accuracy",    
                 "short_passing", "volleys","dribbling",    
                 "curve", "free_kick_accuracy" ,"long_passing",    
                 "ball_control","acceleration","sprint_speed",    
                 "agility","reactions","balance",    
                 "shot_power","jumping","stamina",    
                 "strength","long_shots","aggression",    
                 "interceptions","positioning","vision",    
                 "penalties", "marking","standing_tackle",
                 "sliding_tackle","gk_diving","gk_handling",    
                 "gk_kicking","gk_positioning","gk_reflexes")

for (i in column_names){
  k = paste(i, "Bucket",sep="_")
  player_atts[k] = 
    cut(player_atts[[i]], breaks = 5, labels=c('low','low-med','med','med-high','high'))
}

player_atts <- select(player_atts, c(1:9, overall_rating_Bucket:gk_reflexes_Bucket))
player_atts = player_atts[, -c(5,6)]
all_match <- select(all_match, c(id:away_team_goal, home_player_1:away_player_11, opponent:away_ply_pos_11))

#######
# match_g <- gather(all_match, player, player_id, home_player_1:away_player_11, na.rm = TRUE)
# View(match_g)
# match_s <- arrange(match_g, match_api_id, player)
# View(match_s)
# #match_s <- select(match_s, c(1:10, player, player_id))

# colnames(match_s)[37] <- "player_api_id"

#HP1
match_player <- merge(x = all_match, y=player_atts,by.x='home_player_1',by.y='player_api_id',all.x=TRUE)
match_player$date.x<-ymd_hms(match_player$date.x)
match_player$date.y<-ymd_hms(match_player$date.y)
match_player$time_diff <- difftime(match_player$date.x, match_player$date.y,units='days')
match_player = match_player[match_player$time_diff >= 0,]
match_player_1 = match_player %>%
  group_by(match_api_id, home_player_1) %>%
  filter(time_diff == min(time_diff))
for (i in 61:98){
  colnames(match_player_1)[i] = paste(colnames(match_player_1)[i], "hp_1", sep = "_")
}
for (i in 61:98){
  match_player_1[[i]] = paste(match_player_1[[i]],match_player_1[[36]],sep="_")
}
match_player_1$time_diff=NULL
# HP2

match_player2 <- merge(x = match_player_1, y=player_atts,by.x='home_player_2',by.y='player_api_id',all.x=TRUE)
match_player2$date.x<-ymd(match_player2$date.x)
match_player2$date<-ymd_hms(match_player2$date)
match_player2$time_diff <- difftime(match_player2$date.x, match_player2$date,units='days')
match_player2 = match_player2[match_player2$time_diff >= 0,]
match_player2 = match_player2 %>%
  group_by(match_api_id, home_player_2) %>%
  filter(time_diff == min(time_diff))
for (i in 102:139){
  colnames(match_player2)[i] = paste(colnames(match_player2)[i], "hp_2", sep = "_")
}
for (i in 102:139){
  match_player2[[i]] = paste(match_player2[[i]],match_player2[[37]],sep="_")
}
match_player2$time_diff=NULL
match_player2$id.y = NULL
match_player2$date.y=NULL
match_player2$date=NULL
match_player2$id.x=NULL
##
#HP3

match_player3 <- merge(x = match_player2, y=player_atts,by.x='home_player_3',by.y='player_api_id',all.x=TRUE)
match_player3$date.x<-ymd(match_player3$date.x)
match_player3$date<-ymd_hms(match_player3$date)
match_player3$time_diff <- difftime(match_player3$date.x, match_player3$date,units='days')
match_player3 = match_player3[match_player3$time_diff >= 0,]
match_player3 = match_player3 %>%
  group_by(match_api_id, home_player_3) %>%
  filter(time_diff == min(time_diff))
for (i in 139:176){
  colnames(match_player3)[i] = paste(colnames(match_player3)[i], "hp_3", sep = "_")
}
for (i in 139:176){
  match_player3[[i]] = paste(match_player3[[i]],match_player3[[37]],sep="_")
}
match_player3$time_diff=NULL
match_player3$id.y = NULL
match_player3$date.y=NULL
match_player3$date=NULL
match_player3$id.x=NULL
match_player3$player_fifa_api_id=NULL

#HP4

match_player4 <- merge(x = match_player3, y=player_atts,by.x='home_player_4',by.y='player_api_id',all.x=TRUE)
match_player4$date.x<-ymd(match_player4$date.x)
match_player4$date<-ymd_hms(match_player4$date)
match_player4$time_diff <- difftime(match_player4$date.x, match_player4$date,units='days')
match_player4 = match_player4[match_player4$time_diff >= 0,]
match_player4 = match_player4 %>%
  group_by(match_api_id, home_player_4) %>%
  filter(time_diff == min(time_diff))
for (i in 176:213){
  colnames(match_player4)[i] = paste(colnames(match_player4)[i], "hp_4", sep = "_")
}
for (i in 176:213){
  match_player4[[i]] = paste(match_player4[[i]],match_player4[[38]],sep="_")
}
match_player4$time_diff=NULL
match_player4$id.y = NULL
match_player4$date.y=NULL
match_player4$date=NULL
match_player4$id.x=NULL
match_player4$id=NULL
match_player4$player_fifa_api_id.x=NULL
match_player4$player_fifa_api_id.y=NULL
#HP5

match_player5 <- merge(x = match_player4, y=player_atts,by.x='home_player_5',by.y='player_api_id',all.x=TRUE)
match_player5$date.x<-ymd(match_player5$date.x)
match_player5$date<-ymd_hms(match_player5$date)
match_player5$time_diff <- difftime(match_player5$date.x, match_player5$date,units='days')
match_player5 = match_player5[match_player5$time_diff >= 0,]
match_player5 = match_player5 %>%
  group_by(match_api_id, home_player_5) %>%
  filter(time_diff == min(time_diff))
for (i in 213:250){
  colnames(match_player5)[i] = paste(colnames(match_player5)[i], "hp_5", sep = "_")
}
for (i in 213:250){
  match_player5[[i]] = paste(match_player5[[i]],match_player5[[39]],sep="_")
}
match_player5$time_diff=NULL
match_player5$id.y = NULL
match_player5$date.y=NULL
match_player5$date=NULL
match_player5$id.x=NULL
match_player5$id=NULL
###
#HP6
match_player6 <- merge(x = match_player5, y=player_atts,by.x='home_player_6',by.y='player_api_id',all.x=TRUE)
match_player6$date.x<-ymd(match_player6$date.x)
match_player6$date<-ymd_hms(match_player6$date)
match_player6$time_diff <- difftime(match_player6$date.x, match_player6$date,units='days')
match_player6 = match_player6[match_player6$time_diff >= 0,]
match_player6 = match_player6 %>%
  group_by(match_api_id, home_player_6) %>%
  filter(time_diff == min(time_diff))
for (i in 252:289){
  colnames(match_player6)[i] = paste(colnames(match_player6)[i], "hp_6", sep = "_")
}
for (i in 252:289){
  match_player6[[i]] = paste(match_player6[[i]],match_player6[[40]],sep="_")
}
match_player6$time_diff=NULL
match_player6$id.y = NULL
match_player6$date.y=NULL
match_player6$date=NULL
match_player6$id.x=NULL
match_player6$id=NULL
match_player6$player_fifa_api_id.x=NULL
match_player6$player_fifa_api_id.y=NULL

#HP7
match_player7 <- merge(x = match_player6, y=player_atts,by.x='home_player_7',by.y='player_api_id',all.x=TRUE)
match_player7$date.x<-ymd(match_player7$date.x)
match_player7$date<-ymd_hms(match_player7$date)
match_player7$time_diff <- difftime(match_player7$date.x, match_player7$date,units='days')
match_player7 = match_player7[match_player7$time_diff >= 0,]
match_player7 = match_player7 %>%
  group_by(match_api_id, home_player_7) %>%
  filter(time_diff == min(time_diff))
for (i in 289:326){
  colnames(match_player7)[i] = paste(colnames(match_player7)[i], "hp_7", sep = "_")
}
for (i in 289:326){
  match_player7[[i]] = paste(match_player7[[i]],match_player7[[41]],sep="_")
}
match_player7$time_diff=NULL
match_player7$id.y = NULL
match_player7$date.y=NULL
match_player7$date=NULL
match_player7$id.x=NULL
match_player7$id=NULL
match_player7$player_fifa_api_id.x=NULL
match_player7$player_fifa_api_id.y=NULL

#HP8
match_player8 <- merge(x = match_player7, y=player_atts,by.x='home_player_8',by.y='player_api_id',all.x=TRUE)
match_player8$date.x<-ymd(match_player8$date.x)
match_player8$date<-ymd_hms(match_player8$date)
match_player8$time_diff <- difftime(match_player8$date.x, match_player8$date,units='days')
match_player8 = match_player8[match_player8$time_diff >= 0,]
match_player8 = match_player8 %>%
  group_by(match_api_id, home_player_8) %>%
  filter(time_diff == min(time_diff))
for (i in 326:363){
  colnames(match_player8)[i] = paste(colnames(match_player8)[i], "hp_8", sep = "_")
}
for (i in 326:363){
  match_player8[[i]] = paste(match_player8[[i]],match_player8[[42]],sep="_")
}
match_player8$time_diff=NULL
match_player8$id.y = NULL
match_player8$date.y=NULL
match_player8$date=NULL
match_player8$id.x=NULL
match_player8$id=NULL
match_player8$player_fifa_api_id.x=NULL
match_player8$player_fifa_api_id.y=NULL

#HP9
match_player9 <- merge(x = match_player8, y=player_atts,by.x='home_player_9',by.y='player_api_id',all.x=TRUE)
match_player9$date.x<-ymd(match_player9$date.x)
match_player9$date<-ymd_hms(match_player9$date)
match_player9$time_diff <- difftime(match_player9$date.x, match_player9$date,units='days')
match_player9 = match_player9[match_player9$time_diff >= 0,]
match_player9 = match_player9 %>%
  group_by(match_api_id, home_player_9) %>%
  filter(time_diff == min(time_diff))
for (i in 365:402){
  colnames(match_player9)[i] = paste(colnames(match_player9)[i], "hp_9", sep = "_")
}
for (i in 365:402){
  match_player9[[i]] = paste(match_player9[[i]],match_player9[[43]],sep="_")
}
match_player9$time_diff=NULL
match_player9$id.y = NULL
match_player9$date.y=NULL
match_player9$date=NULL
match_player9$id.x=NULL
match_player9$id=NULL
match_player9$player_fifa_api_id.x=NULL
match_player9$player_fifa_api_id.y=NULL

#HP10
match_player10 <- merge(x = match_player9, y=player_atts,by.x='home_player_10',by.y='player_api_id',all.x=TRUE)
match_player10$date.x<-ymd(match_player10$date.x)
match_player10$date<-ymd_hms(match_player10$date)
match_player10$time_diff <- difftime(match_player10$date.x, match_player10$date,units='days')
match_player10 = match_player10[match_player10$time_diff >= 0,]
match_player10 = match_player10 %>%
  group_by(match_api_id, home_player_10) %>%
  filter(time_diff == min(time_diff))
for (i in 402:439){
  colnames(match_player10)[i] = paste(colnames(match_player10)[i], "hp_10", sep = "_")
}
for (i in 402:439){
  match_player10[[i]] = paste(match_player10[[i]],match_player10[[44]],sep="_")
}
match_player10$time_diff=NULL
match_player10$id.y = NULL
match_player10$date.y=NULL
match_player10$date=NULL
match_player10$id.x=NULL
match_player10$id=NULL
match_player10$player_fifa_api_id.x=NULL
match_player10$player_fifa_api_id.y=NULL

#HP11
match_player11 <- merge(x = match_player10, y=player_atts,by.x='home_player_11',by.y='player_api_id',all.x=TRUE)
match_player11$date.x<-ymd(match_player11$date.x)
match_player11$date<-ymd_hms(match_player11$date)
match_player11$time_diff <- difftime(match_player11$date.x, match_player11$date,units='days')
match_player11 = match_player11[match_player11$time_diff >= 0,]
match_player11 = match_player11 %>%
  group_by(match_api_id, home_player_11) %>%
  filter(time_diff == min(time_diff))
for (i in 441:478){
  colnames(match_player11)[i] = paste(colnames(match_player11)[i], "hp_11", sep = "_")
}
for (i in 441:478){
  match_player11[[i]] = paste(match_player11[[i]],match_player11[[45]],sep="_")
}
match_player11$time_diff=NULL
match_player11$id.y = NULL
match_player11$date.y=NULL
match_player11$date=NULL
match_player11$id.x=NULL
match_player11$id=NULL
match_player11$player_fifa_api_id.x=NULL
match_player11$player_fifa_api_id.y=NULL

#AP1

match_player12 <- merge(x = match_player11, y=player_atts,by.x='away_player_1',by.y='player_api_id',all.x=TRUE)
match_player12$date.x<-ymd(match_player12$date.x)
match_player12$date<-ymd_hms(match_player12$date)
match_player12$time_diff <- difftime(match_player12$date.x, match_player12$date,units='days')
match_player12 = match_player12[match_player12$time_diff >= 0,]
match_player12 = match_player12 %>%
  group_by(match_api_id, away_player_1) %>%
  filter(time_diff == min(time_diff))
for (i in 478:515){
  colnames(match_player12)[i] = paste(colnames(match_player12)[i], "aw_p_1", sep = "_")
}
for (i in 478:515){
  match_player12[[i]] = paste(match_player12[[i]],match_player12[[46]],sep="_")
}
match_player12$time_diff=NULL
match_player12$id.y = NULL
match_player12$date.y=NULL
match_player12$date=NULL
match_player12$id.x=NULL
match_player12$id=NULL
match_player12$player_fifa_api_id.x=NULL
match_player12$player_fifa_api_id.y=NULL
#AP2
match_player13 <- merge(x = match_player12, y=player_atts,by.x='away_player_2',by.y='player_api_id',all.x=TRUE)
match_player13$date.x<-ymd(match_player13$date.x)
match_player13$date<-ymd_hms(match_player13$date)
match_player13$time_diff <- difftime(match_player13$date.x, match_player13$date,units='days')
match_player13 = match_player13[match_player13$time_diff >= 0,]
match_player13 = match_player13 %>%
  group_by(match_api_id, away_player_2) %>%
  filter(time_diff == min(time_diff))
for (i in 517:554){
  colnames(match_player13)[i] = paste(colnames(match_player13)[i], "aw_p_2", sep = "_")
}
for (i in 517:554){
  match_player13[[i]] = paste(match_player13[[i]],match_player13[[47]],sep="_")
}
match_player13$time_diff=NULL
match_player13$id.y = NULL
match_player13$date.y=NULL
match_player13$date=NULL
match_player13$id.x=NULL
match_player13$id=NULL
match_player13$player_fifa_api_id.x=NULL
match_player13$player_fifa_api_id.y=NULL

#AP3
match_player14 <- merge(x = match_player13, y=player_atts,by.x='away_player_3',by.y='player_api_id',all.x=TRUE)
match_player14$date.x<-ymd(match_player14$date.x)
match_player14$date<-ymd_hms(match_player14$date)
match_player14$time_diff <- difftime(match_player14$date.x, match_player14$date,units='days')
match_player14 = match_player14[match_player14$time_diff >= 0,]
match_player14 = match_player14 %>%
  group_by(match_api_id, away_player_3) %>%
  filter(time_diff == min(time_diff))
for (i in 554:591){
  colnames(match_player14)[i] = paste(colnames(match_player14)[i], "aw_p_3", sep = "_")
}
for (i in 554:591){
  match_player14[[i]] = paste(match_player14[[i]],match_player14[[48]],sep="_")
}
match_player14$time_diff=NULL
match_player14$id.y = NULL
match_player14$date.y=NULL
match_player14$date=NULL
match_player14$id.x=NULL
match_player14$id=NULL
match_player14$player_fifa_api_id.x=NULL
match_player14$player_fifa_api_id.y=NULL

#AP4
match_player15 <- merge(x = match_player14, y=player_atts,by.x='away_player_4',by.y='player_api_id',all.x=TRUE)
match_player15$date.x<-ymd(match_player15$date.x)
match_player15$date<-ymd_hms(match_player15$date)
match_player15$time_diff <- difftime(match_player15$date.x, match_player15$date,units='days')
match_player15 = match_player15[match_player15$time_diff >= 0,]
match_player15 = match_player15 %>%
  group_by(match_api_id, away_player_4) %>%
  filter(time_diff == min(time_diff))
for (i in 593:630){
  colnames(match_player15)[i] = paste(colnames(match_player15)[i], "aw_p_4", sep = "_")
}
for (i in 593:630){
  match_player15[[i]] = paste(match_player15[[i]],match_player15[[49]],sep="_")
}
match_player15$time_diff=NULL
match_player15$id.y = NULL
match_player15$date.y=NULL
match_player15$date=NULL
match_player15$id.x=NULL
match_player15$id=NULL
match_player15$player_fifa_api_id.x=NULL
match_player15$player_fifa_api_id.y=NULL

#AP5
match_player16 <- merge(x = match_player15, y=player_atts,by.x='away_player_5',by.y='player_api_id',all.x=TRUE)
match_player16$date.x<-ymd(match_player16$date.x)
match_player16$date<-ymd_hms(match_player16$date)
match_player16$time_diff <- difftime(match_player16$date.x, match_player16$date,units='days')
match_player16 = match_player16[match_player16$time_diff >= 0,]
match_player16 = match_player16 %>%
  group_by(match_api_id, away_player_5) %>%
  filter(time_diff == min(time_diff))
for (i in 630:667){
  colnames(match_player16)[i] = paste(colnames(match_player16)[i], "aw_p_5", sep = "_")
}
for (i in 630:667){
  match_player16[[i]] = paste(match_player16[[i]],match_player16[[50]],sep="_")
}
match_player16$time_diff=NULL
match_player16$id.y = NULL
match_player16$date.y=NULL
match_player16$date=NULL
match_player16$id.x=NULL
match_player16$id=NULL
match_player16$player_fifa_api_id.x=NULL
match_player16$player_fifa_api_id.y=NULL
#AP6
match_player17 <- merge(x = match_player16, y=player_atts,by.x='away_player_6',by.y='player_api_id',all.x=TRUE)
match_player17$date.x<-ymd(match_player17$date.x)
match_player17$date<-ymd_hms(match_player17$date)
match_player17$time_diff <- difftime(match_player17$date.x, match_player17$date,units='days')
match_player17 = match_player17[match_player17$time_diff >= 0,]
match_player17 = match_player17 %>%
  group_by(match_api_id, away_player_6) %>%
  filter(time_diff == min(time_diff))
for (i in 669:706){
  colnames(match_player17)[i] = paste(colnames(match_player17)[i], "aw_p_6", sep = "_")
}
for (i in 669:706){
  match_player17[[i]] = paste(match_player17[[i]],match_player17[[51]],sep="_")
}
match_player17$time_diff=NULL
match_player17$id.y = NULL
match_player17$date.y=NULL
match_player17$date=NULL
match_player17$id.x=NULL
match_player17$id=NULL
match_player17$player_fifa_api_id.x=NULL
match_player17$player_fifa_api_id.y=NULL
#AP7
match_player18 <- merge(x = match_player17, y=player_atts,by.x='away_player_7',by.y='player_api_id',all.x=TRUE)
match_player18$date.x<-ymd(match_player18$date.x)
match_player18$date<-ymd_hms(match_player18$date)
match_player18$time_diff <- difftime(match_player18$date.x, match_player18$date,units='days')
match_player18 = match_player18[match_player18$time_diff >= 0,]
match_player18 = match_player18 %>%
  group_by(match_api_id, away_player_7) %>%
  filter(time_diff == min(time_diff))
for (i in 706:743){
  colnames(match_player18)[i] = paste(colnames(match_player18)[i], "aw_p_7", sep = "_")
}
for (i in 706:743){
  match_player18[[i]] = paste(match_player18[[i]],match_player18[[52]],sep="_")
}
match_player18$time_diff=NULL
match_player18$id.y = NULL
match_player18$date.y=NULL
match_player18$date=NULL
match_player18$id.x=NULL
match_player18$id=NULL
match_player18$player_fifa_api_id.x=NULL
match_player18$player_fifa_api_id.y=NULL
#AP8
match_player19 <- merge(x = match_player18, y=player_atts,by.x='away_player_8',by.y='player_api_id',all.x=TRUE)
match_player19$date.x<-ymd(match_player19$date.x)
match_player19$date<-ymd_hms(match_player19$date)
match_player19$time_diff <- difftime(match_player19$date.x, match_player19$date,units='days')
match_player19 = match_player19[match_player19$time_diff >= 0,]
match_player19 = match_player19 %>%
  group_by(match_api_id, away_player_8) %>%
  filter(time_diff == min(time_diff))
for (i in 745:782){
  colnames(match_player19)[i] = paste(colnames(match_player19)[i], "aw_p_8", sep = "_")
}
for (i in 745:782){
  match_player19[[i]] = paste(match_player19[[i]],match_player19[[53]],sep="_")
}
match_player19$time_diff=NULL
match_player19$id.y = NULL
match_player19$date.y=NULL
match_player19$date=NULL
match_player19$id.x=NULL
match_player19$id=NULL
match_player19$player_fifa_api_id.x=NULL
match_player19$player_fifa_api_id.y=NULL
#AP9
match_player20 <- merge(x = match_player19, y=player_atts,by.x='away_player_9',by.y='player_api_id',all.x=TRUE)
match_player20$date.x<-ymd(match_player20$date.x)
match_player20$date<-ymd_hms(match_player20$date)
match_player20$time_diff <- difftime(match_player20$date.x, match_player20$date,units='days')
match_player20 = match_player20[match_player20$time_diff >= 0,]
match_player20 = match_player20 %>%
  group_by(match_api_id, away_player_9) %>%
  filter(time_diff == min(time_diff))
for (i in 782:819){
  colnames(match_player20)[i] = paste(colnames(match_player20)[i], "aw_p_9", sep = "_")
}
for (i in 782:819){
  match_player20[[i]] = paste(match_player20[[i]],match_player20[[54]],sep="_")
}
match_player20$time_diff=NULL
match_player20$id.y = NULL
match_player20$date.y=NULL
match_player20$date=NULL
match_player20$id.x=NULL
match_player20$id=NULL
match_player20$player_fifa_api_id.x=NULL
match_player20$player_fifa_api_id.y=NULL
#AP10
match_player21 <- merge(x = match_player20, y=player_atts,by.x='away_player_10',by.y='player_api_id',all.x=TRUE)
match_player21$date.x<-ymd(match_player21$date.x)
match_player21$date<-ymd_hms(match_player21$date)
match_player21$time_diff <- difftime(match_player21$date.x, match_player21$date,units='days')
match_player21 = match_player21[match_player21$time_diff >= 0,]
match_player21 = match_player21 %>%
  group_by(match_api_id, away_player_10) %>%
  filter(time_diff == min(time_diff))
for (i in 821:858){
  colnames(match_player21)[i] = paste(colnames(match_player21)[i], "aw_p_10", sep = "_")
}
for (i in 821:858){
  match_player21[[i]] = paste(match_player21[[i]],match_player21[[55]],sep="_")
}
match_player21$time_diff=NULL
match_player21$id.y = NULL
match_player21$date.y=NULL
match_player21$date=NULL
match_player21$id.x=NULL
match_player21$id=NULL
match_player21$player_fifa_api_id.x=NULL
match_player21$player_fifa_api_id.y=NULL
#AP11
match_player22 <- merge(x = match_player21, y=player_atts,by.x='away_player_11',by.y='player_api_id',all.x=TRUE)
match_player22$date.x<-ymd(match_player22$date.x)
match_player22$date<-ymd_hms(match_player22$date)
match_player22$time_diff <- difftime(match_player22$date.x, match_player22$date,units='days')
match_player22 = match_player22[match_player22$time_diff >= 0,]
match_player22 = match_player22 %>%
  group_by(match_api_id, away_player_11) %>%
  filter(time_diff == min(time_diff))
for (i in 858:895){
  colnames(match_player22)[i] = paste(colnames(match_player22)[i], "aw_p_11", sep = "_")
}
for (i in 858:895){
  match_player22[[i]] = paste(match_player22[[i]],match_player22[[56]],sep="_")
}
match_player22$time_diff=NULL
match_player22$id.y = NULL
match_player22$date.y=NULL
match_player22$date=NULL
match_player22$id.x=NULL
match_player22$id=NULL
match_player22$player_fifa_api_id.x=NULL
match_player22$player_fifa_api_id.y=NULL

################# ARules ##################
# all the matches that lose
loss_match = match_player22
### lose as home play, need to use away player attributes in the next steps
home_loss_match = loss_match[loss_match$opponent == loss_match$away_team_api_id,]
home_loss_ar = home_loss_match %>%
  select(preferred_foot_aw_p_1:gk_reflexes_Bucket_aw_p_11, result)
home_loss_ar = home_loss_ar[,-c(1,2)]
home_loss_ar = subset(home_loss_ar, select = -player_fifa_api_id)
### lose as away play, need to use home player attributes in the next steps
away_loss_match = loss_match[loss_match$opponent == loss_match$home_team_api_id,]
away_loss_ar = away_loss_match %>%
  select(preferred_foot_hp_1:gk_reflexes_Bucket_hp_11, result)
away_loss_ar = away_loss_ar[,-c(1,2)]
colnames(away_loss_ar) = colnames(home_loss_ar)
all_loss_ar = rbind(home_loss_ar, away_loss_ar)
##### add column name to values
column_names = names(all_loss_ar)

for (column in column_names) {
  all_loss_ar[[column]] = paste(column, all_loss_ar[[column]], sep = '_')
}

###### delete player numbers
for (i in 1:418) {
  for (j in 1:287) {
    all_loss_ar[j,i] = gsub('_aw_p_[0-9]', '', all_loss_ar[j,i])
  }
}
for (i in 1:418) {
  for (j in 1:287) {
    all_loss_ar[j,i] = gsub('[0-9]', '', all_loss_ar[j,i])
  }
}


write.csv(all_loss_ar,'napoli.csv')
```

```{r, include=FALSE, message=FALSE, results="hide"}
napoli_all3 = read.transactions("napoli.csv", format = "basket",
                           sep = ",", rm.duplicates = TRUE, skip =1, header = FALSE)
# inspect(napoli_all3)
# itemInfo(napoli_all3)
rules <- apriori(napoli_all3, parameter = list(supp = 0.2, conf = 0.3), appearance = list(rhs = 'result_loss'))

rules_lift = sort(rules,by='lift',decreasing = TRUE)

```
  
  When we run the associations of player attributes that correspond to Napoli's loss, we found the following rules:  
  
```{r, fig.width=16}
inspect(rules_lift[1:10])
```

```{r}
# plot(rules_lift[1:5], method = 'graph', engine = 'htmlwidget')
plot(rules_lift[1:10], method = 'paracoord', title = "Parallel Coordinates plot for Napoli's Loss")
```

##### Recommendations against Napoli

Against Napoli, a combination of technical defenders and mid-fielders who can finish yields the best resutls

As an alternative, taking the possesion of the ball in the mid-field helps as well. So a long pass from keeper to the mid-field and mid-fielders with good jumping ability helps to maintain possession.


### Other Recommendations

We also see that in recent seasons (2012 onwards), Roma's performance tends to drop during the middle of the campaign. While this may be due to fatigue towards the christmas period or the lack of practice during the  wintery holiday season, a week long training camp at a warmer climate can help improve the match fitness of the players as well as set the rhythm for the reminder of the season. This may also be helpful in getting the better start to the second half of the campaign compared to our rivals who go sluggish.


